\documentclass[char]{Silversiders}
\parindent=0pt
\begin{document}
\name{\cBeauty{}}
\bigquote{``But he who dares not grasp the thorn should never crave the rose.''}{- Anne Bronte}

You are Arctura cad'Aska, and you are no one's pretty thing. Though it's not for lack of others trying to claim you. The feeling of yearning eyes burning into your back is a strange one. You do not understand it, even now that you are more visually appealing to those around you than you were when you were young. When you were still in your Bulb community's study circles, you were plain and scrawny. Sometimes they would even call you an "ugly duckling." Now, ugly you understood. Ugly was the other children tormenting ice gulls, or pulling each other's hair. You were not ugly. As for "duckling", who knew what that old phrase meant? Perhaps the answers lay in Silverside, in the Perfects' archives, but you knew even as a child that the temptations of the city were forbidden fruit. 

You didn't stay an ugly duckling in the eyes of those around you. By the time of your exit from the study circles, people began to look at you differently, with a sort of hunger that you couldn't understand. You had seen these looks before, as the students around you began to fancy each other and sneak away with each other. By adulthood, you understood lust, to some degree, but not this other thing, that thing that supposedly existed between most of the long term relationships in your community, including your three parents. Eventually you worked up the courage to have some frank conversations with them, and they told you that some people don't form the kinds of ties that were a mystery to you, but that there were other ways of finding connection and happiness. They encouraged you to visit some of the larger Bulb communities, that there were more happily single adults, as well as non-romantic family groupings. Some people are inherently aromantic, they said, and you latched onto the word and held onto it. There was a word for what you were feeling!

Unfortunately, there remained many people who didn't want to accept your newly discovered identity, and pined after you for years. You lost friendships over it. And when friendships were all you wanted (you weren't the kind of aromantic that wanted any sort of long term partnership), that really hurt. In the end, you moved out of your small community and into a larger hub, finding single housing fairly easily. You made a living making, patching and embellishing clothing. You didn't earn much, but it was better than working in the sewers or the factories.

At some point you realized that people were drawn to you in a way that was unnatural, even for those whose experience of romantic love was naturally strong. You knew you had outgrown the "ugly duckling" stage and had become a great beauty, as those in your home community had called you, but something felt off about this. When a stranger caught your gaze and immediately spent their entire month's paycheck to buy you an expensive bauble you had briefly inspected, you began obscuring your eyes in public. That seemed to help, but not entirely.



You felt such relief amongst the Peacekeepers, that you were wanted for something other than your appearance. And they offered you answers to some of your childhood questions about the city and its secrets. Their oral scriptures told of so many things that had been kept from most Silversiders, even most Perfects. The present order of things was a mistake, but the Savior who had founded the city would return someday to make things right. These strange powers of yours were a gift from her, and you knew you were meant for more than looking pretty. You began to see the beauty shining out from amongst all the ugliness, or at least the potential for beauty.

It made perfect sense to you, that violence only bred more ugliness. You thought back to your childhood, and the cruelties even children could propagate. That was not the way. You would learn to control the beauty you radiated, channel it into changing Silverside without the ugliness of violence.

Turn down all those who pursue you for love (aromantic, immune to love magic)

Become known for something other than your appearance. Show them all that promoting beauty is more than just skin deep

If it?s not, seek the beauty you feel whispering to you in the silence. It calls itself Silverside, and it?s enticing, yet Silverside itself seems almost devoid of beauty at this point. Seek it either way.

Can see ghosts

\begin{itemz}[Goals]
	\item Determine whether the beauty of this world is truly gone and worth saving. 
	\item Seek social justice for Shades and Bulbs without violence.
	\item Seek the "Silverside" that isn't the city.
	\item Find a genuine friend who isn't out for a romantic relationship.
	\item Reach out to the powerful presence of Love in the building to help you find friendship and keep away romantic pursuers.
	\item Recruit for the Peacekeepers.
\end{itemz}

\begin{itemz}[Notes]
	\item If you see a blue headband, you're seeing a ghost!
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
