\documentclass[char]{Silversiders}
\parindent=0pt
\begin{document}
\name{\cLove{}}
\bigquote{``We accept the love we think we deserve.''}{- Stephen Chbosky, The Perks of Being a Wallflower}

Your parents never thought you would amount to anything. Neither did your teachers. And now the fellows of your form spit at your feet as you walk up the steps to the Council building. But you are stronger and cleverer than you look, and one day it will all be worth this pretense. Because underneath the hard exoskeleton you show to the world, you care enough to sacrifice your own happiness for the greater good. Because, however fucked up the world you live in is, you love those close to you, love the potential for good in humanity. It's a fierce love, no softness around the edges, but love nonetheless. Someday, maybe you'll be able to indulge in softness, but for now you use your apparent frailty, lack of substance, and vulnerability to manipulate to your advantage.

You grew up in one of the more affluent neighborhoods that Shades were allowed to reside in. Your parents had become complacent with their lot long before your were born. They worked as secretaries in government buildings, cleaning up the Perfects' spills, filing their paperwork, answering their mail. Something broke them when they were still young, hardened their dreams and hopes for something better, leaving them as shells of what they could have been. You could see it in them, and they could tell that you could see it in them, which they resented. While you were an unassuming child, you were stubborn to a fault, which made things worse for you. There's a part of you that knew even then that they intended to protect you by so harshly devaluing your nature, to ensure that the harsh world didn't destroy you. They were too exhausted by living in that world to be softer. Still, your stubbornness meant that you never gave up, despite the odds. You kept at your schoolwork, playing the long game to prove everyone wrong.

When you came of age, you transformed from an unassuming child to an androgynous beauty, taking the pronouns they/them. Some nonbinary Silversiders express their gender as some mixture of man and woman, something else entirely, or some fluidity between these, but you feel your nonbinary-ness as a distinct lack of gender. Still, you almost smile when people have trouble placing you when you meet; it is a small euphoria in a life that gives you a little levity. However, it took time to get used to the fact that your looks made people stare. There is still some prejudice in Silverside that assumes that beauty and cleverness are unlikely to coexist, so people's tendencies to underestimate you only increased. You decided to use that to your advantage, intending to shock everyone when you surpassed them all. Still, even then you only idealistically planned to figure out how to get a better job than your parents.

You were 18 years old the year everything changed.

First, you crossed paths with the Historians. You were in the last year of your secondary education, in a training rotation with a shopkeeper in a pawn shop, when the strange old Bulb came into the shop, running \cHonor{\their} hands over many of the older objects. You almost opened your mouth to object, but something stopped you. When \cHonor{\they} touched some items, \cHonor{\their} eyes drifted off, as if \cHonor{\they} was seeing something far away, then \cHonor{\they} scribbled something in a small notebook. \cHonor{\They} brought those items to the front, and paid for them. They were very pricy, but the \cHonor{\human} seemed to have no qualms about spending such an amount. You must have been staring, because \cHonor{\they} smiled at you and said, "I see you are curious. You are interested in the history of Silverside, are you not?" You had been, somewhat, but this suddenly made you \emph{very} curious. You nodded your head silently. Your mask dropped, and you looked towards the notebook with obvious curiosity. "You are especially observant," said the Bulb, "but you need to work on your subtlety. I could help you with that, and satisfy your curiosity."



Servant of the Council
Use your abilities to get in the good graces of the Council of Perfection to convince them to treat Shades and Bulbs equally
If that fails, make them sick with love to someone who will never return the feelings
Improve your powers to make this possible/permanent
Don?t actually fall in love with anyone whose intentions are not good, but find love soon (you have the sense that something terrible has the potential to ruin everyone?s love)
Figure out more about why you have powers
Don?t let the Council learn you?re part of The Resistance
You?ve had dreams about a great love, long long ago. You?ve heard the names Arqara and Desiderata. Learn more about it, why it?s relevant still (and eventually do what you can to bring back that love)
(You probably want to talk to the other Historians, but they think you?re a bit silly and useless and will have other priorities)

\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
