\documentclass[char]{Silversiders}
\parindent=0pt
\begin{document}
\name{\cMuscle{}}
\bigquote{``As I see it, part of the art of being a hero is knowing when you don't need to be one anymore.''}{- Alan Moore, Watchmen}

The Academy of Perfection never managed to twist your spirit, though your teachers tried many times to get you to embrace the power you were supposedly born to wield. But despite your imposing presence, you never let their cruelty into your heart. From a very young age you have been a gentle giant... at least in your intentions. Your earliest memory is of trying to keep a frost moth as a pet. You kept it in a glass jar with plenty of soft moss and lichen. But your large clumsy fingers kept slipping and touching its fragile wings, until it could no longer fly. One morning the moth was still. You wept. Your icy parents saw this as weakness, and they scolded you to get you to harden your tender heart. After all, you were destined for greatness, perhaps even a spot on the Council of Perfection. Tender hearts would do no good in this harsh world we live in, where one emotional decision could be the difference between power and revolt, life and death. But you refused to accept this, even after you were sent away at the age of five to board at the Academy.

And your teachers at the Academy certainly tried to bring out your harsh side, but in doing so they taught you that there was something horribly wrong with the world you lived in. By the time you started using \cMuscle{\they}/\cMuscle{\them} pronouns at the age of 12, you spent a lot of time escaping into the tunnels beneath the school and visiting parts of the city you weren't supposed to go. You saw families very different from your own "Perfect" one. Shade families laughing together as they patched up the walls of their tenements. Bulb families shopping together in the outer markets. Though they seemed much more tired than elite Perfect families, there was love there. You caught on very quickly that the reason they were so tired was because of the people like your family.

That made you angry, but not the kind of anger that led your parents to treat you with disdain. This was an anger at the unfairness of your society, and a desire to change things. Not that you understood how to do that, though. By the time you were nearing adulthood, the teachers had nearly given up on you, merely keeping you at the school because of how rich your parents were. Nearly every night you snuck out into the city, wearing a mask to hide all but your eyes. You wanted it to be obvious that you were a perfect doing good deeds to help those of other forms, and your eyes would show that, but not reveal your identity. Or so you thought.

In reality, during your attempts at being a vigilante, trying to scare off other Perfects who sought to inflict cruelties on others who didn't have the power to fight back, you were a bigger version of your childhood self, your clumsy hands and clumsy actions often causing more harm than good. While your intent was noble, in your estimations, you just didn't understand the reality of the power dynamics involved, or the consequences of your own ignorance. In trying to save others, you were centering yourself, trying to be a hero and assuming that those you were trying to save were incapable of saving themselves.

The authorities tended to bring you into their custody rather than anyone you were trying to stop, and those you were trying to help would slip away as fast as they could. The few times they didn't, they drew the disdain of the authorities no matter how many times you tried to explain who was in the wrong. It was lucky that no one you were trying to help ever ended up hurt. The authorities would return you to the Academy and leave you to the teachers for punishment.

When you were 17, you tried one too many times to perfect your vigilantism, and got yourself kicked out of the Academy. To some degree, it was a relief. But, on the other hand, it gave you a slight taste of what it was like to not live under the protection of the elite. Your parents disowned you, of course. You had to find an apartment, despite knowing very little about earning a living the hard way. Luckily you were as strong as ever, and were quickly hired as a construction worker. It was enough to keep your new apartment and keep you fed, but it was still a massive reality check for you. Silverside was a lot more complex than you had ever really considered. And it would continue to get even more incomprehensible.

Figure out how to be a hero
Social justice for shades and bulbs
Figure out the source of your powers
Figure out who the Peacekeepers are, and maybe join them, depending on what you find
Seek out the Historians to learn more about the history of your world?s racism
Join the Resistance
Use your powers to make things ?right?
See if you can find anything that helps you become a better hero, however you define that

\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
