\documentclass[char]{Silversiders}
\parindent=0pt
\begin{document}
\name{\cTruth{}}
\bigquote{``In a time of deceit telling the truth is a revolutionary act.''}{- George Orwell}

You are \cTruth{}, Perfect and \cTruth{\offspring} of \cDeath{\full}, head of the Council of Perfection. Even among the children of the most powerful in Silverside, you occasionally get stares at the Academy. But it's not like you could have any influence on \cDeath{\them}. Your \cDeath{\parent} currently doesn't think too highly of you, or maybe \cDeath{\they} would visit you more like the other parents of boarding students. Maybe you wouldn't be a boarding student at all. And of course, there's the fact that your \cDeath{\parent} is literally evil and trying to destroy the world. How's that for dysfunctional family? 

But even before you figured that out, you knew that \cDeath{\their} mind was on other things than raising you. That task was left entirely to the Shade servants, as your mother died in childbirth. Your rarely ever saw \cDeath{\them} smile. But on such occasion stood out more than any other such rare moment. It was once when \cDeath{\they} thought you weren't looking. \cDeath{\They} had a book in his hands, a very old book. Books were rare. You knew that even as a child. This one was pure white, bound in leather from the albino calves that were raised deep in the caverns as food for the rich. You didn't know that part then. \cDeath{\They} looked at it and smiled as \cDeath{\they} read. You hid until \cDeath{\they} left the study, then you snuck into the room and found the book on \cDeath{\their} desk. You opened it up and flipped through the pages, only to drop the book in horror. The pages were filled with engravings of dead animals and old humans: some shriveled, some vivisected, some reduced to bone. You ran from the room, leaving the book open on the desk. The next day the book was gone. It was never spoken of, because of course it wasn't. Your \cDeath{\parent} never deigned to speak with you about \cDeath{\their} secrets.

You were seven years old when you were sent away to the Academy of Perfection. You never really fit in with the other Perfect students from the ruling families. As you got older, it became apparent that you cared so little about the things that meant so much to them. Appearance, reputation, deportment, power. You just wanted to draw in your sketchbook and read fanciful stories of heroes and adventure, or sneak out through the tunnels beneath the school and go swimming in the ice pools on the edge of the city. It was doing the latter that you met \cWisdom{}. \cWisdom{\They} had a bag of rags. No, clothes. \cWisdom{\They} were washing dirty clothes in the clear ice pools, gazing into realms of imagination as \cWisdom{\they} did the task by rote. When you appeared, \cWisdom{} didn't look away, like many Shades did in the presence of upper class Perfects. \cWisdom{\They} looked at you plainly. Angrily. It was love at first sight for eleven year old \cTruth{}.

When you made no demands of \cWisdom{\them}, just going ahead with your swimming, eventually \cWisdom{} began to speak with you. Gradually, over the course of many times sneaking out, you became close friends, and eventually \cWisdom{\they} fell in love back. You spent many hours sitting atop the Glass Cathedral with \cWisdom{\them}, watching the sunset and talking into the night. That was where \cWisdom{\they} and several other homeless members of the underclass slept at night. It was a beautiful place, but had a negative reputation among Perfects. Thus, none of them ever caught you there with \cWisdom{}.

You'd always felt something was wrong about how Shades and Bulbs were treated in Silverside, but hearing from \cWisdom{} about how badly people were really being treated and the horrors of their workplaces made you angry. You began to speak out in classes in favor of equality. That earned you many punishments from your teachers. "If you love the Shades so much, why don't you work like one?" Then they would assign you to cleaning or dish washing. The joke was on them though, because this only led you to sympathize with the Shades and Bulbs even more.

When you reached the age of 17, your the beginning of your last year at the Academy, something changed. You knew, of course, that change would come eventually, that you would be expected to enter Perfect high society, romance another Perfect, have Perfect children. But this wasn't that change coming early. This was something else entirely. Something... unnatural. You thought it was hallucinations at first, that you were catching some sort of fever. You imagined something in a daydream, and suddenly it was there. And before you could be more than shocked, it would vanish. That, and your hunger for knowledge grew sevenfold. And lastly, it seemed that sometimes you could compel people to give truthful answers to your questions against their own will.

And it wasn't just you. \cWisdom{} confided to you that \cWisdom{\they} was also experiencing manifestations of unnatural power. \cWisdom{\They} could weave bewitching words to convince people of any argument and even enhance your own power. You began to explore what you could do together, and gradually began to gain some semblance of control over your strange gifts. 

That was several months ago. A week ago, the Knights found you.

Daughter of the leader of the Council
Mok love plot, opposed by Magnus
Join the Knights of the Silverside
Find out what ?Silverside? means
Maintain the balance and restore the Story - after induction
After induction - recruit
Keep the world from ending again
Discover why the world keeps ending
Bring about the return of Loyalty - after induction
Discover who you are
Figure out your powers
Do hero shit, despite not being the Savior
Support Mok's goals

Can see ghosts

\begin{itemz}[Goals]
	\item 
\end{itemz}

\begin{itemz}[Notes]
	\item If you see a blue headband, you're seeing a ghost!
\end{itemz}

\begin{contacts}
	\contact{\cTest{}} <- This is the format for contacts 
\end{contacts}

\end{document}
