\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bAcademy{}}

If you have this sheet, you attended or currently attend the Academy of Perfection, the premier educational institution for young Perfects set to inherit the leadership of the city of Silverside. The attendance of the Academy fluctuates depending on the year, but generally is between 100 and 300 students between the ages of 5 and 18 years.

The Academy educates its students in governance, mathematics, writing, reading, deportment, mechanical and scientific theory, aetherics, and city history. Students like to say that they are also trained in ruthlessness, falsehood and spite. This too is true.

Students may be said to have a strong bond amongst themselves, at least during their younger years, but by the later classes it is more common to see cutthroat rivalry. However, despite these rivalries, which can extend beyond the psychological and emotional, Academy students generally will defend each other when faced up against a non-Academy-educated threat. Academy education is a trial by fire, and nearly all students and graduates can at least find common ground in having made it through this gauntlet.

There are, however, exceptions to the rule. Some students fail out. Rarer still are the students who maintain a kind heart and moral compass and still manage to graduate. All of these are generally seen as outsiders by the general population, though the latter are reluctantly assigned to city positions, particularly if their parentage is high.

All students are aware of the secret tunnels beneath the school leading into the rest of the city, though they quickly learn to deny it to their teachers, lest they get their fingers switched. Learning to lie is part of any Academy education. As a result of sneaking through these tunnels during their formative years, most Academy-educated Perfects are much more comfortable navigating beneath the city than their non-Academy counterparts.

\end{document}
