\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bBulbs{}}

If you have this sheet, you were born a Bulb, one of the three forms of humanity living in the city of Silverside. You are a descendent of old humanity, though you look the least like them of the three forms. The skin of all Bulbs are some shade of blue, from pale sky blue to deepest indigo, and hair colors range from black to blue to brightest white (which tends to take on a greenish tinge due to the presence of algae.) All Bulbs also have bioluminescent spots and stripes on their skin in a variety of fluorescent shades. You can control their glow at will, enough to see in the darkest of caverns. Bulbs have no ability for flight, and are referred to as "lead-footed" for this perceived lack of grace, and for barely being able to jump off the ground. However, you are the best at swimming of any form, due to your webbed fingers and toes. Like Perfects, you have gills, but generally make far greater use of them. As Bulbs spend a lot of time underwater, most wear skintight waterproof suits. For fashion's sake, some adorn these suits with sparkling stones and icefish scales.

Bulbs are banned by the Council of Perfection from living in the city of Silverside proper. Instead, you live in the underwater ice caves on the outskirts of the city. For the most part, the other forms leave your part of the city alone. For the Shades, this makes sense, as they have no gills. But Perfects generally look down on your abodes, so different from their fancy, technologically advanced city accommodations. Perfects generally will not enter the ice caves unless there is some sort of raid by law enforcement. Sometimes, they come in for seemingly no reason, just to leave you on edge. They call your homes dens of lawlessness, but this couldn't be further from the truth.

Bulbs are restricted by the Council of Perfection to working the least desirable of jobs by Perfect standards, those in the dank and dark places that the rest of the city doesn't like to think about, yet are necessary to keep the city running. Many Bulbs stay entirely within Bulb society, not considering it worth taking one of these jobs. Instead, they fill roles such as storytellers, community cooks, clothing makers, fisherpeople, and dwelling carvers. This is looked down upon by the Perfects, who ensure that their undesirable jobs are filled by threats of imprisonment. As long as these jobs are filled by Bulbs, though, anyone else is generally overlooked. Bulbs decide communally who is the most fit to take these jobs to avoid weak or disabled Bulbs from being forced into dangerous positions.

Bulb society is fairly insular and has taken a very different path from the forms living in the city proper. Bulbs live communally. While each family grouping has their own private sleeping space, 5-25 families generally have shared communal living, cooking, and eating areas. Bulbs, like Shades, are also more likely to be accepting of non-reproductive family groupings, who generally take in the children of those killed in dangerous workplace environments or elsewhere. Asexuality and aromanticism are considered normal. Unlike in Perfect society, not contributing in some way to a reproductive family grouping is socially acceptable. However, while not having a partnership as an adult is considered normal, living outside of a shared community is not.

It is still common to see an asexual third or fourth member of a romantic partnership who contributes to raising children or a grouping with an aromantic, yet reproductive partnership, but this is just as common as seeing non-reproductive groupings with one or more asexual members. Divorce is also socially acceptable among Bulbs, and more common than among Perfects due to the stigma against it in their society, which views divorce as detrimental to raising children unless the continuation of a family grouping creates an environment that hinders their development. Divorcees generally stay in the same community, even if they don't have children, as there is usually housing for single people. Abusive community members will be ejected, though.

All Bulbs have family names beginning with the prefix "cad". Other than that, family names may be seen across forms, as all in Silverside descended from a single population. Family names are passed on not according to gender, but are given to children according to whichever parent is most prominent in their field. 

When referring to those of the other forms, Perfects often refer to groups according to their form's family name prefix ("becs" or "cads"). Originally neutral, though somewhat informal, this terminology can take on a dismissive tone when used to say that all among a form share some negative trait. The terms themselves are not slurs, though, and each form generally takes pride in their family name prefix. In fact, Bulbs have taken to using "cads" as an informal term for those of their form they are close to (i.e. "us cads") and calling Perfects "abs" behind their backs, which the Perfects consider insultingly informal when it comes from the forms they oppress.

Though it is rare, occasionally children will be born of mixed parentage, though it is illegal for Shades and Bulbs to make unions with Perfects. What happens to these children depends on a variety of factors. 
To Shades, any child of such a union is welcome among them, though this is not how they are treated by Perfects. To Perfects, appearance and powers are everything. If someone has all the visible traits and abilities of a Perfect and none of the visible traits of another form (extra abilities are usually overlooked), they will be considered a Perfect. 

It sometimes takes years to determine this, in which case a child will stay with their Perfect parent and be observed. If an ambiguous child is birthed by a non-Perfect parent with no Perfect parent willing to claim them, they will be taken away to be observed in a medical facility. If it is determined that the child is a Perfect, they will either stay with their Perfect parent or be assigned to Perfect family of lesser prominence. If it is determined the child is a Bulb, they will go to their Bulb parent or be delivered to a random Bulb community.

Perfects care little about the children of mixed Bulb/Shade parentage, though Bulbs and Bulb-appearing people are not allowed to live in Silverside proper by Council of Perfection order. There is no law against such unions, but they are difficult to maintain due to the Shades' lack of gills and inability to live in Bulb communities. Some of these families decide to strike out on their own and establish themselves outside of the city proper AND the Bulb communities. The children of these unions generally choose the family name prefix that feels right to them.

\end{document}
