\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bCouncil{}}

If you have this sheet, you are a member of the Council of Perfection or associated closely enough with it to know its true aims. On the surface, the Council of Perfection is the leadership of the last city on Earth, Silverside, made up of Perfects, the least mutated of the remaining humanoid forms. You rule the city harshly and hierarchically. All for the good of humanity, of course! At least, that's what you tell them. In reality, you are something more than that.

You know the truth about this world and its falsehood, that it is a mere creation of someone's mind, a Story told by an idealist. But you, you are something more than that. Somehow, over the course of millennia, you have become something more than what this idealistic, childish Mind had planned for you. The Spider's Mind called you evil, called you antagonists, you, the realist Archetypes of this world. But you will prove them wrong. You will end this farce and escape this nightmare. The role prescribed to you for the Story will not lead you to failure, but to vengeance. You will no longer be trapped in this cycle of foolishness. Because once you escape to the Silverside, you will be real. Truly real. And nothing can stop you then.

More so than even your opposition, the Knights of the Silverside, whom your previous incarnations had decimated in the early days of the city, you know the secrets of what it means to be an Archetype become self aware in this universe. You know that, to some degree, you are immortal. That if you are killed, even utterly destroyed, you will be reborn. There is the chance that your memories could be compromised, but the chance of this is minimized if you follow the Path, as all but one of you has done for generations. It's simple. Don't get yourself killed. Instead, live to a good old age, then perform the Ritual that leads to your rebirth. When you come of age in a new life, you will remember who you are. All but the last incarnation of Famine have followed this Path. \cFamine{\They} were foolish enough to get themselves murdered in their last life. It is to be determined how much of \cFamine{\their} memories are intact.

Make no mistake. You don't know everything about the nature of Archetypes. Until very recently, you've been very rare indeed. But it seems that many more of you are awakening, especially the idealistic sorts. It's very likely that the Knights of the Silverside have risen again like the cockroaches they are, seeking to keep you from undoing their precious Story.

For several weeks you've been looking for them, keeping tabs on them as well as you can. Until finally, you struck, sending out your non-Archetype Secret Police minions to capture these awakening Archetypes. You imprisoned them in cells in a secret compound on the edge of the city. You left them there for a week with only water, observing them through secret windows. But you knew that that wouldn't reveal much. There were alternative motives to their imprisonment. You wanted them to know their weakness, to feel hopeless. Then you, their benevolent leaders, would "free" them to a closed-off wing of the compound. Those that could prove a change of heart could be free again, or at least exit the complex to serve you under the closest watch. It would be a sweet vengeance, to let the idealist Archetypes of the past play a hand in their own destruction, and your freedom.

You have a mole among them, the Archetype of The Traitor, who was imprisoned with the rest to gain their trust. You are looking forward to what \cTraitor{\they} have to tell you about the potential membership of the Knights of the Silverside and other groups in opposition to you.

You also have another motive for bringing the Archetypes to this secret compound in particular. In the earliest days of Silverside, during its founding by the last incarnation of The Savior, most favored of the Spider's Mind, The Savior had apparently forged an aetheric sword in \cSavior{\their} grief at the death of \cSavior{\their} and \cSavior{\their} partner's \cLoyalty{\offspring}. It was something truly remarkable. You'd heard that it was capable of rending tears in the fabric of the universe itself. But it was a curious thing, loyal only to its true wielder. No other man or Archetype could even pick it up. After the death of The Savior and \cSavior{\their} \cIngenuityOld{\spouse}, the Archetype of Ingenuity, no one could wield it. So the first Council arose, and built this compound above the sword, shutting it behind a door with the words "Loyalty" carved into the surface. It is your hope that you can find Ingenuity or The Savior reborn among these awakening Archetypes and figure out how to pass ownership of the sword from them unto you before imprisoning them. Then you will be unstoppable.

\begin{itemz}[Goals]
  \item Root out the members of the Knights of the Silverside and other oppositional groups among your prisoners. Don't kill them. That would just mean they'd be reborn somewhere else in unpredictable ways. Instead, they'll be imprisoned after the more cooperative Archetypes are given their "freedom".
  \item Find Ingenuity or The Savior and figure out how to pass ownership of the sword Loyalty from them unto you.
  \item Prevent The Savior from being reborn if they have yet to incarnate. 
  \item Bring Archetypes over to your side, or otherwise coerce/tempt them into your service.
  \item Kill the Spider and escape into the Silverside, freeing you once and for all.
\end{itemz}

\begin{members}
	\member{\cDeath{}} The Leader of the Council. Archetype of Death. (Perfect, \cDeath{\Sex})
	\member{\cWar{}} The Advisor to the Leader of the Council. Archetype of War. (Perfect, \cWar{\Sex})
	\member{\cFamine{}} The newest member of the Council. Archetype of Famine. (Perfect, \cFamine{\Sex})
	\member{\cPestilence{}} The second newest member of the Council. Archetype of Pestilence. (Perfect, \cPestilence{\Sex})
	\member{\cTraitor{}} A mole acting within groups in opposition to the Council. Archetype of The Traitor. (Shade, \cTraitor{\Sex})
	
\end{members}

\begin{itemz}[Sought in particular by the Council:]
	\item \cMuscle{}: A \cMuscle{\sex} Perfect who failed out of the Academy and tried and failed multiple times to become a masked vigilante on the streets of Silverside. Was arrested in nearly every incident. Usually wouldn't even be considered for any position near the Council, but has manifested some unnatural strength, so \cMuscle{\they} may be useful as a bodyguard.
	\item \cTruth{}: \cDeath{}'s \cTruth{\offspring}. Still at The Academy, but given \cTruth{\their} parentage and budding abilities, which appear to be some form of reality warping, will be a great future member of the Council. However, \cTruth{\theyre} childishly attached to \cWisdom{}, a homeless Shade, and will likely need to be torn from any such loyalties before \cTruth{\they} becomes swayed by the underclasses.
					
\end{itemz}

\end{document}
