\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bCult{}}

If you have this sheet, you are a cultist of The Cult of the Architect. As a cultist, you know that our world is one of many, potentially infinite worlds. In recent generations, the Cult arose after small riftss in reality began to open up around Silverside. Most Silversiders would instinctually avoid these rifts, but the founders of the Cult were drawn to them. Through these rifts, they saw into the infinite of The Silverside. After staring for a long, long time, something stared back. That something was an Architect, a mighty creator of universes.

The Cult of the Architect sprung up to serve the Architect, in the hope that it would one day be possible to bring it into our world. Because while the rifts in the universe had led you to your god, they were also a harbinger of destruction. Only an Architect could save this world. And your Architect in particular promises to be a benevolent ruler, with you at their right hand. Already your Architect has given you power. 

\cenquote{But all power comes at a cost.}

As the whisperings of the Architect have told you, time is running out for your universe, and you must use your powers to acquire a human sacrifice to finally let the Architect through. Otherwise, you are well and truly doomed.

\cWar{}, your high priestess, concocted a plan to find the perfect sacrifice. \cWar{\They} had told you in advance of \cWar{\their} plan. You were "captured" and "imprisoned" during a raid on individuals who have likely also been peering through the rifts, as they seem to have attracted powers of their own. Such individuals are apparently the most appealing to the Architect.

You were released into a secret compound after a week had passed. It was tough, as \cWar{} said it would be, but necessary. \cWar{\They} said the Council members there, including \cWar{\them}, will say something different, a cover story that \cWar{\they} has fed to them to convince them to allow this special gathering. Then, it will be up to you to gain your potential sacrifices' trust, and choose the perfect one. Because this night is special, and the sacrifice must be performed tonight. It will be difficult to do in secrecy, but it is our duty to do it.

If you can, you must also do what you can to bring in those who might be sympathetic to your cause. You have a few in mind, but you must be careful even speaking to them, for if they disapprove of your actions, all could be for nought!

Lastly, \cWar{} has told you that the building you are in houses a mighty weapon that can rend the fabric of the universe enough to send your sacrifice through, empowering the Architect to come in. It is the sword called Loyalty, imbued with aetheric power. Supposedly only those with the right to it can touch it, unless ownership is passed on to another. It is your job to figure out who has the right to Loyalty, and how to transfer that right to your high priestess so the ritual can be completed.

\begin{itemz}[Goals]
  \item Find the sword Loyalty and figure out how to transfer its ownership to \cWar{}.
  \item Find a potential sacrifice. Gain their trust, then lure them away and perform the ritual to bring the Architect into our world.
  \item Cautiously recruit others to your cause.
  \item Don't let anyone get in your way, especially the leader of the Council, \cDeath{}.
\end{itemz}

\begin{itemz}[Greensheets]
  \item \gSummoning{}
\end{itemz}

\begin{members}
	\member{\cWar{}} High priestess of The Cult of the Architect. (Perfect, \cWar{\Sex})
	\member{\cOracle{}} Cultist and Oracle of the Architect. (Bulb, \cOracle{\Sex})
	\member{\cTrickster{}} Cultist. (Shade, \cTrickster{\Sex})
	
\end{members}

\begin{itemz}[Some Potential Recruits]
	\item \cFamine{}: A \cFamine{\sex} Perfect. The newest member of the Council, still figuring out \cFamine{\their} place in things.
	\item \cPestilence{}: A \cPestilence{\sex} Perfect. A seasoned member of the Council. Be very cautious, as \cPestilence{} seems fairly set in \cPestilence{\their} ways, though not to the degree of \cDeath{}, who you must not risk approaching.
	\item \cTraitor{}: A \cTraitor{\sex} Shade. You can't get a read on this one. But you sense that \cTraitor{\they} may be adrift, looking for a cause to support.
	
\end{itemz}

\begin{itemz}[Some Potential Sacrifices]
	\item \cMuscle{}: A strong, powerful \cMuscle{\sex} Perfect.
	\item \cOutcast{}: A \cOutcast{\sex} Bulb with no loved ones.
	\item \cBeauty{}: A beautiful \cBeauty{\sex} Shade.

\end{itemz}

\end{document}
