\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bHistorians{}}

If you have this sheet, you are a member of The Historians. The Historians are a group of Silverside citizens concerned with the preservation of artifacts related to city history and particularly the world before the end. You do what you can to piece together what the world used to be like, and how it ended. There's lots of gaps in this chain of events, even with the artifacts you've managed to collect, and some things are surely only guesses, but you still feel that it is your duty to humanity to make these educated guesses and preserve the past.

Occasionally, you encounter artifacts with a spark of aetheric energy. Your Leader, Min'oo cad'Aska, figured out a way to access the history of these items through tapping into this energy. All it takes for a Historian initiated in this art is to hold the artifact, and they will see a vision of a fragment of its past, held in the aetheric energy.

Perhaps tapping into this energy did something to you, because all but the Council member among you were caught up by the secret police for displaying unnatural abilities. You were taken to a secret compound on the edge of the city and imprisoned for a week, given only water. Then, they let you all out to mingle, and the Council of Perfection walked in. Perhaps said Council member has some explaining to do.

However, you've heard whispers that artifacts of the old world are stored in facilities like this one, which you have been imprisoned in. This could prove to be a valuable opportunity to learn more about them and take notes. Each of you have been assigned a Historian Notebook to take notes on these items. If the artifacts are stored in a secret part of the compound, though, it may be difficult to get your hands on them, particularly while you're prisoners. But when else would you have such access to such a secretive location? You must take advantage of it.

\cenquote{Because lately, more and more artifacts have been singing to you. They don't tell a pretty story.\\ And those who forget the past are doomed to repeat it.}

Here are some things that the artifacts have whispered into the minds of the most trusted among you:
\begin{itemz}
	\item The family names have nothing to do with form or prominence, or at least they didn't originally. They're the names of places, of nations within a nation.
	\item The End that led to the founding of your city was not the first, but only the most recent in a string of apocalypses.
	\item Even your End was made up of a dizzying amount of separate events. The fact that they coincided is curious to you, and speaks of a power beyond coincidence.
	\item Each apocalypse has coincided with the rise of someone who calls themselves The Savior, a presumptuous title for someone who always fails to stop the apocalypse.
	\item Silverside was founded by such a "Savior", a \cSavior{\human} by the name of \cSavior{\full} and \cSavior{\their} \cIngenuityOld{\spouse}, \cIngenuityOld{\full}.
	\item They betrayed the city, and the Council arose in their place and fulfilled the role of safeguarding humanity that the couple had failed at.
\end{itemz}

\begin{itemz}[Goals]
	\item Acquire (or at least examine) as many artifacts from the old city or before the End as you can, filling out your Historian Notebooks.
	\item Use this information to determine whether old mistakes are being repeated.
	\item Figure out a way out of this situation when you've gotten your historical data.
	\item Perhaps recruit from among these unusual folks, or enquire about their own potential experiences with the aetheric energy in artifacts.
\end{itemz}

\begin{members}
	\member{\cHonor{}} A member in high standing. (Bulb, \cHonor{\Sex})
	\member{\cLove{}} A member in high standing. (Shade, \cLove{\Sex})
	\member{\cWisdom{}} A member. (Shade, \cWisdom{\Sex})
	\member{\cPestilence{}} A member, ashamedly. (Perfect, \cPestilence{\Sex})
	
\end{members}

\begin{itemz}[Sought by The Historians, for Recruitment or Questioning]
	\item \cBeauty{}: A \cBeauty{\sex} Bulb. Seems interested in the nature of the city.
	\item \cWar{}: A \cWar{\sex} Perfect. One of the Council of Perfection. Seems interested in the history of wars. Approach very cautiously.
	\item \cOutcast{}: A \cOutcast{\sex} Bulb. A Bulb who lives alone in the Wastes. Maybe \cOutcast{\they} has discovered artifacts out there.
	\item \cFamine{}: A \cFamine{\sex} Perfect. A curious new member of the Council.

\end{itemz}

\end{document}
