\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bInitiates{}}

If you have this sheet, you are an initiate of the Knights of the Silverside. Recently, masked figures sought you out when you were alone in the city. They pulled you aside and told you things that only you could have known: your secrets, the strange POWERS you'd been gradually learning to control for the past few months. They had powers too, which they showed you as you stared in awe, and they had chosen you because you were special, uniquely able to maintain the balance in a society on the edge and leaning towards evil.

They said some things you don't understand. Yet. They said that you would understand, should you choose to become initiated into the Knights of the Silverside. The way they greeted you... "Hail, Archetype!" It had sent shivers down your spines. Because there was something strangely familiar about the words. They told you that they existed to restore and protect the "Story". You don't know what that means either, but, like the greeting, it taunted you with its familiarity. Also, why did they call themselves The Knights of THE Silverside? Why not The Knights of Silverside? Perhaps it was some remnant of the old ways of language, from the earlier days of the city.

Most importantly, they told you, that you must be incredibly careful to never tell anyone about the Knights. They said that anyone, even those we held most dear, could be trying to stop them. That if they learned who we truly were, and that we were initiating with the Knights, our lives could be in danger.

Of course you said yes. When you agreed to be initiated, they took off their masks and let you see their faces. Then they let you know about each other. Of course, you'd known each other since childhood, and something didn't surprise you that both of you were chosen.

They said they'd be back to begin the initiation. But that hadn't happened. Only a few days later the Council's secret police had snatched you from the streets. You spent a week in a cell before being let out with the others into the closed-off wing of the secret compound. To your shock, your recruiters were there as well, apparently prisoners as well. You need to figure out some way to talk to them in private. This must be the evil they had warned you about!

\begin{itemz}[Goals]
  \item Don't let your captors or those working with them figure out that you're associated with the Knights.
  \item Find a way to talk to your recruiters in private.
\end{itemz}

\begin{members}
	\member{\cTruth{}} An initiate. (Perfect, \cTruth{\Sex})
	\member{\cWisdom{}} An initiate. (Shade, \cWisdom{\Sex})
	
\end{members}

\begin{members}[Full Members]
	\member{\cHonor{}} Leader of the Knights of the Silverside. (Bulb, \cHonor{\Sex})
	\member{\cTraitor{}} A member. (Shade, \cTraitor{\Sex})
	
\end{members}

\end{document}
