\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bKnights{}}

If you have this sheet, you are a full member of the Knights of the Silverside. You are a member of a secret organization that has existed since before the end, and before the end before that, made up of Archetypes of this world's Story become self aware. You serve a noble purpose in this world, keeping the balance between good and evil, with a goal to restore and protect the Story of the Spider's Mind, thus protecting the Mind and everyone still living within it, as well as the Spider itself. 

You aren't alone in this task, as the Spider's Mind is not the only such world, or the only type of world in the Multiverse. You call yourself the Knights of the Silverside in unity with similar such organizations across the multiverse, because safeguarding a Spider's Mind protects the integrity of the Silverside at large. If evil Archetypes become self aware were to escape the Spider's Mind and infect other universes like a cancer... similar apocalypses could plague those worlds too, and perhaps even destroy them, as is the danger for this world. Yes, the apocalyptic cycle in this world has begun to make reality unstable. One more and the Spider's Mind could unravel entirely. That's why your role is so important.

Your role is not easy. Many have lost their lives and animate forms fighting this fight, but Archetypes can only be entirely destroyed by the end of the universe. You have a habit of coming back in some form or another. Hence why recruitment of Archetypes who have lost their memories and been reborn is such a priority. Especially when the Council of Perfection has been taken over entirely by evil Archetypes.

And the fact that so little of your organization's old knowledge still lives within you is an issue. The old leadership was decimated in the old days of Silverside, and you only have scraps of their knowledge. Many Archetypes have been missing for generations. But recently you have been able to identify many Archetypes newly awakening to their powers. It's too early to know what Archetypes they are, but something big is happening. Soon. Too early soon. The Savior Archetype hasn't even been born yet. This could be a disaster.

So you collected all your notes on awakening Archetypes and reached out to two of the most promising, most young and passionate to begin the initiation process. But it seems you may have been too late. Days later you were snatched off the street by the Council's Secret Police and imprisoned. A week later you were brought to a closed-off wing of the secret compound that is your prison. Everyone there is an Archetype... including the four Council members in there with you. Your initiates are also there. You can only hope they haven't said anything to the Council. It was a gamble reaching out to \cTruth{}, the daughter of the leader of the Council of Perfection. But she's been living as a boarding student at the Academy of Perfection. And acting out. Rebelling against the system. You hope you haven't made the wrong decision. Because it seems that everything could come to a head here, at the edge of the last city in the world.

You must do what you can to initiate \cTruth{} and \cWisdom{} without the Council becoming aware. Many of the other Archetypes on your list are here as well. It's incredibly risky, but you must do what you can to bring them in as well, even in this environment. Then, no matter what the cost, you must end this in your favor. The universe and all living in it are depending on you.

\begin{itemz}[Goals]
  \item Don't let your captors or those working with them figure out that you're members of the Knights.
  \item Find a way to initiate as many Archetypes into the Knights as possible. Find those with the most useful powers and the most idealism.
  \item Figure out a way to stop whatever nefarious plot the Council has to end the world one final time.
\end{itemz}

\begin{itemz}[Miscellaneous]
  \item If it is safe to do so, Knights greet each other saying "Hail, Archetype!" or "Hail" and the name of their Archetype.
\end{itemz}

\begin{members}
	\member{\cHonor{}} Leader of the Knights of the Silverside. Archetype of Honor. (Bulb, \cHonor{\Sex})
	\member{\cTraitor{}} A member. Archetype of Stealth.(Shade, \cTraitor{\Sex})
	
\end{members}

\begin{members}[Initiates]
	\member{\cTruth{}} An initiate. (Perfect, \cTruth{\Sex})
	\member{\cWisdom{}} An initiate. (Shade, \cWisdom{\Sex})
	
\end{members}

\begin{itemz}[Potential Recruits]
	\item \cMuscle{}: A \cMuscle{\sex} Perfect.
	\item \cIngenuity{}: A \cIngenuity{\sex} Shade.
	\item \cOutcast{}: A \cOutcast{\sex} Bulb.
	\item \cCaregiver{}: A \cCaregiver{\sex} Bulb.
	\item \cLove{}: A \cLove{\sex} Shade.
	\item \cTrickster{}: A \cTrickster{\sex} Shade.

\end{itemz}

\end{document}
