\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bPeacekeepers{}}

If you have this sheet, you are a member of The Peacekeepers. The Peacekeepers is a quasi-spiritual movement devoted to peace and nonviolent action to restore the city to its original aims of equality, not the authoritarian hell it has become. You have little access to the details of Silverside's history, but stories have been passed down for generations. The Peacekeepers have a strong oral tradition, focusing especially on The Savior, the \cSavior{\human} who founded Silverside and kept it safe against the encroaching apocalypse. The Peacekeepers are devoted to The Savior, believing \cSavior{\they} will hear your prayers and bestow blessings upon \cSavior{\their} most pious and steadfast followers.

The traditions and oral scriptures of The Peacekeepers are quite secretive, only revealed to members, who have disavowed all violence. As you have made this disavowal, the last generation of The Peacekeepers passed on their knowledge to you before their own lives ended.

These are the most sacred stories of your group:
\begin{itemz}
	\item The Savior was more than human. \cSavior{\They} was called upon by the universe itself to save humanity. While \cSavior{\they} were not fully successful, as only one city was saved, even that much would have been impossible without \cSavior{\them}.
	\item The Savior wielded an aetheric sword, called Loyalty, but not for the purpose of violence. It could harm none. In fact, it could only even touch its wielder. But it was a source of great power. In fact, it was The Savior wielding Loyalty that saved the city from the final waves that threatened to sweep away the survivors of the apocalypse gathered at the future site of Silverside. \cSavior{\They} thrust the sword into the ground, sending up a barrier around this place as high as the highest of towers, a shield to protect humanity.
	\item The Savior managed to protect the final thousands of humanity without resorting to violence, and in return the universe granted \cSavior{\them} and \cSavior{\their} \cIngenuityOld{\spouse} Ingenuity, who was also more than human, a gift. From the sword in the quickly freezing ground, a child appeared in its place.
	\item The child Loyalty was like \cLoyalty{\their} parents and the sword they wielded, empowered with aetheric gifts. \cLoyalty{\They} was loved so much by \cLoyalty{\their} parents and all the survivors, or so they thought.
	\item When Loyalty came of age, something terrible happened. The young Silverside was marred by a truly violent act. A member of a group who hungered for power threatened the Aetheric Family. They murdered Loyalty in cold blood, leaving behind the same sword from which \cLoyalty{\they} sprung. Yet none of these violent people could touch it.
	\item Distraught, The Savior and Ingenuity wasted away as the attackers took over control of the city. Their descendants became the Council of Perfection.
	\item The Peacekeepers believe that the Aetheric Family will come again and be reunited, and that it is our duty to ensure their rebirth and to protect them from the Council of Perfection or any other sources of violence.

\end{itemz}

Unfortunately, you'd had few leads as to how or when they would be reborn, or even the location of the sword Loyalty. That is, until several of your members, all blessed by The Savior with powers beyond human, were captured by agents of the Council and imprisoned. When you were let out into a closed-off wing of your prison, you saw a locked door with the word "Loyalty" carved into the steel.

\begin{itemz}[Goals]
  \item Figure out a way to get into the locked room and see if the sword Loyalty is within.
  \item If you find the sword, do whatever you can to prevent the Council from being able to claim it.
  \item Ensure the rebirth of The Savior and Ingenuity, and the return of their child Loyalty from the sword.
  \item Keep the others in this prison from becoming violent. Large displays of violence bring disfavor upon everyone, and will likely lead to the further downfall of Silverside.
  \item It seems that more among you appear to be blessed by the Aetheric Family. See who you might be able to recruit into The Peacekeepers.
\end{itemz}

\begin{members}
	\member{\cCaregiver{}} The leader of The Peacekeepers. (Bulb, \cCaregiver{\Sex})
	\member{\cBeauty{}} A member. (Bulb, \cBeauty{\Sex})
	\member{\cTraitor{}} A member. (Shade, \cTraitor{\Sex})
	
\end{members}

\begin{itemz}[Promising Potential Recruits]
	\item \cTruth{}: A \cTruth{\sex} Perfect.
	\item \cWisdom{}: A \cWisdom{\sex} Shade.
	\item \cLove{}: A \cLove{\sex} Shade.
	\item \cFamine{}: A \cFamine{\sex} Perfect.
	\item \cOutcast{}: A \cOutcast{\sex} Bulb.
	\item \cIngenuity{}: A \cIngenuity{\sex} Shade.
	\item \cHonor{}: A \cHonor{\sex} Bulb.

\end{itemz}

\end{document}
