\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bPerfects{}}

If you have this sheet, you were born a Perfect, one of the three forms of humanity living in the city of Silverside. Though you were once called Skyes in the oldest texts, you are now referred to only as Perfects, as dictated by the Council of Perfection, which rules on high. You are a descendent of old humanity, and look the most like old humanity of all the three forms. You have their skin and hair colors, but have gained the ability to tolerate the cold of the world after the End, breathe under water through gills on the sides of your neck, and fly using the flowing aether in the atmosphere.

Early on, those of your form seized control of Silverside, installing the Council of Perfection into the rulership position over the city. The Council members choose their own successors, and keep their methods to themselves, but they are rumored to have inhuman powers beyond what evolution has provided. Even average Perfects live in fear of the Council's iron fist.

In the decrees of the Council, it is necessary to maintain strict law and order and rigid hierarchy in order to keep humanity alive. As a Perfect, you have access to society's luxuries, such as fine housing with running water and plumbing, aetheric appliances and lights. You are also among those legally permitted to own factories and growing caverns. 

All Perfects have a great deal of privilege in Silverside society, though some have far more power than others, particularly those that are in or connected to the Council of Perfection and/or have graduated from the Academy of Perfection. Though the Council of Perfection rules over all of Silverside, they also set the social standards of Perfect society.

There is some expectation in Perfect society that family groupings be reproductive, but gender and number are not considered of relevance, as long as each member of the family contributes something towards raising the next generation of Perfects. Asexuality and aromanticism are considered normal, as long as those with these identities join some sort of reproductive family grouping. Most commonly, this entails an asexual third or fourth member of a romantic partnership who contributes to raising children or a grouping with an aromantic, yet reproductive partnership. 

The presence of romantic affect is not considered a necessary part of a reproductive partnership, but it is expected that family groupings feel some sort of affection for each other. Perfect society values groupings that stay together at least as long as it takes to raise children to adulthood, so divorce is discouraged unless enmity is creating a poor home environment for children or all of the children are grown and have moved out of their childhood homes. Divorce is also looked down upon as something that is common among the Shades and Bulbs, who are implied to have less stable families and be careless in raising their children.

All Perfects have family names beginning with the prefix "ab". Other than that, family names may be seen across forms, as all in Silverside descended from a single population. Family names are passed on not according to gender, but are given to children according to whichever parent is most prominent in their field. 

When referring to those of the other forms, Perfects often refer to groups according to their form's family name prefix ("becs" or "cads"). Originally neutral, though somewhat informal, this terminology can take on a dismissive tone when used to say that all among a form share some negative trait. The terms themselves are not slurs, though, and each form generally takes pride in their family name prefix. Though perhaps Perfects most of all. Still, it is expected that Perfects be referred to as "Perfects", and not the informal "abs", especially not when it comes from the other forms.

Though it is rare, occasionally children will be born of mixed parentage, though it is illegal for Shades and Bulbs to make unions with Perfects. What happens to these children depends on a variety of factors. To Perfects, appearance and powers are everything. If someone has all the visible traits and abilities of a Perfect and none of the visible traits of another form (extra abilities are usually overlooked), they will be considered a Perfect. 

It sometimes takes years to determine this, in which case a child will stay with their Perfect parent and be observed. If an ambiguous child is birthed by a non-Perfect parent with no Perfect parent willing to claim them, they will be taken away to be observed in a medical facility. If it is determined that the child is a Perfect, they will either stay with their Perfect parent or be assigned to Perfect family of lesser prominence. If it is determined the child is a Shade, they will go to their Shade parent or be sent to an orphanage. If it is determined the child is a Bulb, they will go to their Bulb parent or be delivered to a random Bulb community. 

Perfects care little about the children of mixed Bulb/Shade parentage, though Bulbs and Bulb-appearing people are not allowed to live in Silverside proper by Council of Perfection order. There is no law against such unions, but they are difficult to maintain due to the Shades' lack of gills and inability to live in Bulb communities.

\end{document}
