\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bResistance{}}

If you have this sheet, you are a member of The Resistance. You are an underground network devoted to direct action and other forms of resistance against the tyranny of Silverside's hierarchical society and its so-called "Council of Perfection". You are not against the use of violence, though you prefer your most destructive actions to be to the hearts and minds of the city. Of course, this still necessitates activities performed in the shadows without a trace. You want to be the specter in their nightmares, that can strike when they least expect and retreat into the darkness of the tunnels beneath the city when the deed is done. These are primarily acts of sabotage to their seats of wealth, the factories and their mansions. 

Killing a Council member themselves would not kill their ideology, but only make it stronger. Instead, you aim to plant a new ideology in the minds of the underclasses. That a different world is possible. One where they need not toil for scraps, only to live as second-class citizens. For the underclasses, you show them what it's like to be dangerous. For the Council and their ilk, you show them what it's like to be fearful, to be outnumbered in might and mind.

You have those among you with exceptional aetheric abilities, a likely gift from the same path of evolution that made you so adapted to the icy environment. The Perfects think themselves superior for their forms most similar to those of old humanity. But you know the truth. There is no superior. There is no inferior. Not at least by virtue of one's form. It is what one does with that form that truly matters. So those among you with such abilities have pledged them towards justice for the oppressed, the Shades and Bulbs of Silverside. You are one of those who fight for equity and reparations.

You were still in the early stages of planning your next action when the Council's secret police captured you, taking only those with abilities from the streets and even from their homes. All you were able to learn before they threw you in a cell was that The Resistance was not the target of these raids, but any such individuals with these abilities, including many you'd been scouting as potential recruits. Perhaps the Council saw you as a threat? But there is still hope that your identities as Resistance members have not been revealed.  You must use that to your advantage, and not let them let on that they have the leader of The Resistance in their clutches.

But there is something you are having trouble understanding. In the little time that you've been in the Council's secret compound, no one has interrogated you. No one has been the slightest bit suspicious about The Resistance, despite it having initiated a riot in the streets of Silverside mere days before. It's almost as if they have something else on their minds...

It is best to see that as a boon. It means you are able to gather intelligence from right under their noses, as they have just let you and all the other prisoners out into a closed-off wing of the compound. And it is likely they are hiding something important here in this place. Perhaps you can truly upset their worlds, right here, right now. They won't even see it coming.

\begin{itemz}[Goals]
	\item Gather information from this secret compound and from the Council members themselves that can be used against them. Locations of treasures, Secret Police operations, that sort of thing.
	\item Don't let any of the Council realize who you are, particularly your leader.
	\item Convince as many of those imprisoned with you to join your cause. Most of them are likely quite upset with the Council at this point.
	\item Discover what the Council is hiding. There has got to be some reason that their focus is on corralling people with aetheric abilities rather than the actions of The Resistance.
	\item If you can, sabotage the Council's plans underneath their noses. Just don't get caught.
\end{itemz}

\begin{members}
	\member{\cIngenuity{}} The leader of The Resistance (Shade, \cIngenuity{\Sex})
	\member{\cCaregiver{}} Member (Bulb, \cCaregiver{\Sex})
	\member{\cLove{}} Member (Shade, \cLove{\Sex})
	
\end{members}

\begin{itemz}[Potential Recruits]
	\item \cBeauty{}: A \cBeauty{\sex} Bulb who has spent some time in Silverside proper.
	\item \cTrickster{}: A \cTrickster{\sex} Shade who has managed to elude the Perfects until now despite being involved in some likely questionable dealings.
	\item \cWisdom{}: A \cWisdom{\sex} Shade who appears to be homeless. Likely has reasons to hate the establishment.
	\item \cTraitor{}: A \cTraitor{\sex} Shade. Not much intelligence has been gained on this individual, but as a Shade it is worth talking to \cTraitor{\them}.
	\item \cOracle{}: A \cOracle{\sex} Bulb. Lives in the city proper and has few ties to Bulb culture.
	\item \cHonor{}: A \cHonor{\sex} Bulb who is devoted to preserving Bulb culture.
	\item \cTruth{}: A \cTruth{\sex} Perfect who appears to be connected romantically with \cWisdom{}. The \cTruth{\offspring} of \cDeath{}, head of the Council of Perfection. Young and perhaps idealistic enough to bring to the cause.
	\item \cFamine{}: A \cFamine{\sex} Perfect. The newest member of the Council of Perfection. Sources say that \cFamine{\they} have shown potential disdain for the system. Approach very cautiously.
	\item \cPestilence{}: A \cPestilence{\sex} Perfect. One of the members of the Council of Perfection. Sources say \cPestilence{\they} have a half-sibling who is a Bulb. May sympathize with the cause, but may not. Approach very cautiously.
	\item \cOutcast{}: A \cOutcast{\sex} Bulb outcast from even Bulb society. Lives in the Wastes. May know something useful about what exists outside Silverside or general survival. Quite possibly has nothing to lose.				
\end{itemz}

\end{document}
