\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bShades{}}

If you have this sheet, you were born a Shade, one of the three forms of humanity living in the city of Silverside. You are a descendent of old humanity, and fall between the Perfects and the Bulbs in terms of how much you look like old humanity people. All Shades have dark rings around their eyes, and while their skin can be any color old humanity had, most Shades have bright white or silver hair. Other hair colors are possible among your form, but much less common than in Perfects. Unlike the perfects, you have no gills with which to breathe underwater, and cannot fly, though you can jump high and glide on aetheric currents in the air.

You also have a peculiar ability. Shades are able to perform a kind of ocular hypnosis, to bewitch Perfects and Bulbs and make them do as they desire for a short amount of time. Fellow Shades are immune to this effect. The ability is temporary, and the target of its effect will remember it in full when they are released from its spell. Due to this last fact, there is likely much more fearmongering about the eyes of Shades than there are actual cases of bewitchment. Using ocular hypnosis on Perfects is punishable by imprisonment. There are no laws about its use on Bulbs, though powerful Perfects have been known to compel Shades to use it against them when it is in their favor.

Shades are restricted by the Council of Perfection to the lower or servant class of Silverside, relegated mostly to jobs in the factories and growing caverns, while a select few among you serve the Perfects in their homes and even in the Academy. Your homes are much more humble than those allowed to the Perfects, and usually have no running water or plumbing, aetheric appliances are generally shared across blocks of apartments, and your lighting is restricted to certain hours.

Despite these hardships, Shade society is usually much more warm and caring and based on community support than that of the Perfects. Unlike the Perfects, Shades are likely to be accepting of non-reproductive family groupings, who generally take in the children of those killed in the workplace or elsewhere. Asexuality and aromanticism are considered normal. Unlike in Perfect society, living alone or not contributing in some way to a reproductive family grouping is socially acceptable. 

It is still common to see an asexual third or fourth member of a romantic partnership who contributes to raising children or a grouping with an aromantic, yet reproductive partnership, but this is just as common as seeing non-reproductive groupings with one or more asexual members. Shade families still tend to be larger than those of the Perfects, due to members banding together into chosen families to support each other in the harsh conditions left to them by Perfects. Divorce is also socially acceptable among Shades, and more common than among Perfects due to the stigma against it in their society, which views divorce as detrimental to raising children unless the continuation of a family grouping creates an environment that hinders their development.

All Shades have family names beginning with the prefix "bec". Other than that, family names may be seen across forms, as all in Silverside descended from a single population. Family names are passed on not according to gender, but are given to children according to whichever parent is most prominent in their field. 

When referring to those of the other forms, Perfects often refer to groups according to their form's family name prefix ("becs" or "cads"). Originally neutral, though somewhat informal, this terminology can take on a dismissive tone when used to say that all among a form share some negative trait. The terms themselves are not slurs, though, and each form generally takes pride in their family name prefix. In fact, Shades have taken to using "becs" as an informal term for those of their form they are close to (i.e. "my becs") and calling Perfects "abs" behind their backs, which the Perfects consider insultingly informal when it comes from the forms they oppress.

Though it is rare, occasionally children will be born of mixed parentage, though it is illegal for Shades and Bulbs to make unions with Perfects. What happens to these children depends on a variety of factors. 
To Shades, any child of such a union is welcome among them, though this is not how they are treated by Perfects. To Perfects, appearance and powers are everything. If someone has all the visible traits and abilities of a Perfect and none of the visible traits of another form (extra abilities are usually overlooked), they will be considered a Perfect. 

It sometimes takes years to determine this, in which case a child will stay with their Perfect parent and be observed. If an ambiguous child is birthed by a non-Perfect parent with no Perfect parent willing to claim them, they will be taken away to be observed in a medical facility. If it is determined that the child is a Perfect, they will either stay with their Perfect parent or be assigned to Perfect family of lesser prominence. If it is determined the child is a Shade, they will go to their Shade parent or be sent to an orphanage. 

Perfects care little about the children of mixed Bulb/Shade parentage, though Bulbs and Bulb-appearing people are not allowed to live in Silverside proper by Council of Perfection order. There is no law against such unions, but they are difficult to maintain due to the Shades' lack of gills and inability to live in Bulb communities. Some of these families decide to strike out on their own and establish themselves outside of the city proper AND the Bulb communities. The children of these unions generally choose the family name prefix that feels right to them.

\end{document}
