\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bSilversideCity{}}
\cenquote{``Some say the world will end in fire,\\
Some say in ice.\\
From what I've tasted of desire\\
I hold with those who favor fire.\\
But if it had to perish twice,\\
I think I know enough of hate\\
To know that for destruction ice\\
Is also great\\
And would suffice.''}{- Robert Frost}

You were born in Silverside, the last city on Earth and last bastion of humanity, or what humanity has become. Nearly a thousand years ago, the world ended. They say that its harbinger came from the air, bringing fire, then eruptions from the earth, a deluge of water, and finally a deep freeze that never ended. Your ancestors were drawn to this place, for reasons that have been lost to time. The founders of Silverside, of names unknown, were somehow able to stave off the final waves of the apocalypse and shelter a few thousand souls while untold billions died.

Somehow, life prevailed. But survival came at a cost. The world was a different place after the end. There was something in the air, in the ice, in the frozen soil. The remnants of humanity changed. With each new generation, the people mutated, finally settling into three forms, all able to tolerate their new environment like no man had ever been able to survive before the deep freeze.

The first group, originally called Skyes in the old texts, is today known as the Perfects. While able to tolerate the bitter cold, breathe under water with gills, and fly using the aetheric currents of the air, Perfects are the nearest in appearance to old humanity of the three forms. From early on, Perfects seized the leadership role in Silverside, ruling with a fist of iron from the Council of Perfection. In the eyes of the Council, strict law and order and rigid hierarchy are necessary to keep humanity alive. Perfects have control over the most luxurious housing and own the factories and caverns used to grow food. The children of the most elite among the Perfects attend the Academy of Perfection, learning to take control from the previous generation of elites.

The second group is called the Shades, who live as second-class citizens in Silverside. Shades are immediately recognizable by the dark rings around their eyes. Their skin can be any color a Perfect's skin can be, but they most often have pure white hair. Shades cannot fly, but are able to jump high and glide. Unlike Perfects, Shades have no gills, and are unable to breathe underwater, though they are even more resistant to the cold than Perfects. Perhaps the thing about Shades that leads to the most distrust and hate of their form is their ability to bewitch the other forms with their eyes and make the bewitched do as they desire. However, this effect is temporary, and remembered in full by those who are released from its spell. There is likely much more fearmongering about the eyes of Shades than there are actual cases of bewitchment. Either way, Shades are the lower or servant class of Silverside, and using their bewitchment on Perfects is punishable by imprisonment. Shades are restricted mostly to jobs in the factories and caverns, while a select few serve the Perfects in their homes and even in the Academy.

The third group is called the Bulbs, who are disallowed from living in Silverside proper, but instead spend their lives in underwater caverns on the outskirts of the city. It is considered highly unusual to see them outside of their domain or the dangerous positions they are restricted to, in the dank and dark places that the rest of the city doesn't like to think about, yet are necessary to keep the city running. Bulbs look the least like old humanity. Their skin comes in shades of blue, and their hair colors range from black to blue to vivid white. Bioluminescent spots and stripes freckle across their skin, and they are able to control their glow at will, enough to see in the darkest of caverns. Bulbs have no ability for flight and can barely jump, but they can swim better than any other form. Due to their watery home, most Bulbs wear skintight waterproof suits.

Over the generations, a standardized system of naming has arisen in Silverside, based on form and family. First comes a person's given name, then their form prefix, and finally their family name. The prefix for Perfects is "ab". For Shades, it is "bec". Finally, for Bulbs it is "cad". For example, a Shade named Taren of the Ado family would be called Taren bec'Ado. Family names are not passed down according to gender, but by prominence in their field. When Silversiders unite to form a family, the children take the name of the member who is most prominent in their field of work. Some say there is meaning to the family names, but so much time has passed that few have any idea what they could have meant.

There is some expectation in Perfect society that family groupings be reproductive, but gender and number are not considered of relevance. Shades and Bulbs are more likely to be accepting of non-reproductive groupings, who generally take in the children of those killed in the workplace or elsewhere. Gender is widely understood to be an innate sense of identity separate from reproductive nature. Most individuals identify as male, female, or nonbinary in terms of gender.

The last census of Silverside and its surrounding areas showed a total population of forty thousand souls, with about equal numbers in each of the three forms. Buildings in Silverside are generally painted bright colors in defiance of the sameness of the ice. The buildings frequented by Perfects are powered day-round by aetheric energy sent through wires from a generator that harvests it from the air. Shades may have such wiring, but generally can only afford to power their dwellings for part of a given day. The city overall is built into the side of a mountain, with numerous tunnels snaking inside the mountain and under the city proper.

On the outskirts of the city sits an ancient building known as the Glass Cathedral, though it is neither glass nor a cathedral. Its walls are made of an unknown transparent material as hard as diamond. For the most part, it is an abandoned structure, though homeless Shades are known to shelter there, and some say that cults use it for arcane rituals. Silverside is rumored to have many cults and secret societies, all vying for power and control of the future of humanity.

Beyond the city of Silverside lies the Wastes. Most Silversiders, even Bulbs, avoid venturing into the Wastes at all costs. However, some unlucky souls end up banished to the Wastes Beyond. Given the small number of humans still alive, it generally takes something truly despicable to be given such a punishment.

Lately, there have been more rumors than usual of mysterious, inexplicable occurrences within the city and its outskirts. The Council of Perfection has taken notice, spiriting away anyone suspected of unnatural crimes.

\end{document}
