\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bSpider{}}

You know the secret nature of the world you live in. If most were to hear this truth, they would not believe it, or not want to believe it. Your entire universe is the creation of a single mind and, to some degree, at the mercy of this mind. This being is known as a Spider, and this universe the Spider's Mind. In the same way that a spider is a simple being, capable of creating complex beauties and grotesque deaths within its web without knowing the true depths of its creations, so is the Spider unaware of the depths of it's creation. In fact, it is unlikely that the Spider even knows that its mind and the stories within have birthed a universe tethered to its will.

The Spider's Mind began as a Story with specific components and conditions. A prescribed beginning, middle, end, and the Archetypes of its characters and themes. Then something changed. The Archetypes of the adversaries and threats that once played well with the Story, giving it conflict and pushing it forward, began to become aware of themselves and their situation. They took physical form and saw that the Story was not ultimately in their favor. So they began to work towards radically altering the Story. Instead of ending with a victorious Savior, these Archetypes brought about the apocalypse. Some part of the Spider knew that something was terribly wrong, and the world began to reset itself and recover from the apocalypse. Other Archetypes that were on the other side of the Story began to awaken to their true nature, but always too late. The Archetypes of evil would overtake them every time. The reborn Savior would fail, and the apocalypse would decimate the planet again and again.

All of this is taking a toll on the Spider's Mind, to the point that the Story has become more and more distorted. One more successful apocalypse, and there's a chance that the Spider itself will die, ending the Story permanently, and taking the world with it. This is the goal of the Archetypes of evil, who hope to outlive the Spider's Mind, which has tried to force them into defeat so many times.

But more and more opposing Archetypes are beginning to awaken, some being born and others springing forth from inanimate form. If they manage to restore the Story to its original path, the Savior will prevail, the Spider will live, and the Archetypes of evil will be vanquished as the Spider planned for them to be.

\end{document}
