\documentclass[blue]{Silversiders}
\parindent=0pt
\begin{document}
\name{\bWastes{}}

If you have this sheet, you have knowledge of the Wastes beyond the city of Silverside. No one knows how far they extend, but it's believed that they go on forever, around the entire planet. Thus, banishment to the Wastes is a death sentence. Not from the cold. Humanity has evolved to adapt to that. It's the lack of food that generally gets to you. Unless you are particularly skilled in finding or growing food in the barren landscape of the Wastes, in which case you may be able to eke out a miserable existence.

Banishment to the Wastes isn't a common punishment, at least when it comes to the legal system put in place by the Council of Perfection. Humanity is small in numbers, so it is seen as wasteful unless the crime committed causes more harm than the death of a single person, or if someone is a persistent, unredeemable criminal threat. However, there are also informal banishments within smaller communities within Silverside. If a group is large or powerful enough, they can enforce such a thing, according to their own concepts of a banishable offense.

When a Perfect is banished, they are usually quick to succumb, having been used to being coddled and served. Whereas, Shades or Bulbs especially are much more likely to survive longer, being used to making do despite hardship, and are more willing to do everything it takes to survive, no matter how degrading, like scavenging in the waste pits outside of the city for food.

People who spend a lot of time in the Wastes also tend to learn its secrets, you among them. At first, you wondered if what you saw out there were from hunger-induced hallucinations. But no, you eventually learned that what you were seeing was real. In fact, living in the barren Wastes has primed you to see the things that others might easily overlook... including the rifts in reality that are becoming more and more common. They look like mirages from a distance, but up close, you can see through them into what appears to be other worlds. And beyond that, you have learned how to reach through them and pull things out. The average person doesn't notice such impossible things, let alone have the mental and physical capacity to bring things through. But you do, and you tend not to share that fact, as having such a trick up your sleeve can mean the difference between life and death.

Those who do manage to survive in the Wastes, or those rare souls who choose to venture out there willingly for whatever reason, gain survival skills beyond the knowledge of anyone else in Silverside. Thus, if you have this sheet, you have the following abilities:

\begin{itemz}[Survival Abilities]
	\item \aFirstAid{}
	\item \aTough{}
	\item \aScavenge{}
\end{itemz}

\end{document}
