\documentclass[notebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nHypnosisResearch{}}

\begin{page}{first}
(Pages of this notebook are only readable with a \emph{translator} item unless you know otherwise.)

I was able to sneak a little notebook in here, so I'm going to make use of it to record my research notes on my attempts to enhance natural Shade hypnosis abilities. My goal is to make it possible to bewitch the mind and leave no memory of said bewitchment.

After 10 minutes turn to page \nbref{two}.
\end{page}

\begin{page}{two}
I think the most obvious thing to do first is to find a subject to hypnotize to provide a baseline for my experiments. For science, of course. Strangely, due to these unusual circumstances, it will likely be much easier than usual to get away with using my charm and talent for falsehood.

After you have hypnotized someone and used a test command on your subject, turn to page \nbref{three}.
\end{page}

\begin{page}{three}
Well, that turned out exactly as expected, at least in regards to the hypnosis.

But I've had a hunch for a while that high concentrations of aetheric energy contribute to our mutations. The more aetheric energy in a space, the more likely we are to mutate, even in ways that are heritable. I'm going to test this by having another Shade hold some \iAethericMetal{} for ten minutes (there's got to be some around here somewhere!), then observe them hypnotizing someone and see if their victim remembers it. Best to test this on someone else initially. Safety first!

After you have done this, turn to page \nbref{four}.
\end{page}

\begin{page}{four}
Hmm... the victim of my test subject seemed hazy after being hypnotized, but ultimately remembered it. Perhaps I need to turn up the power. 

I've learned from my time in the Cult of the Architect that strange energies leak into our world through the rifts. I'll try charging the rhythmic metal by holding it within ZoC of a rift for about five minutes. Then I'll wear it on my person for ten minutes.

After you've done this, turn to page \nbref{five}.
\end{page}

\begin{page}{five}
I think I've got it! I feel more powerful than before. Now, I've got to try it out. Something tells me that I've got to use it or lose it.

Retrieve an ability card from the OOG H Packet. You must use the ability within ten minutes of receiving it, or you'll have to follow the instructions on \nbref{four} and \nbref{five} again.

Any Shade who learns of this method can follow the instructions on pages \nbref{four} and \nbref{five} to also enhance their hypnosis ability.
\end{page}

\endnotebook

\end{document}
