\documentclass[greennotebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nIngenuityGreen{}}

\begin{page}{first}
You have a weird headache in this place, a sort of buzzing at your temple. You feel on edge, like something is about to happen. To you. But not because you've been arrested, or because of what the Council has said. That seems almost irrelevant in this moment. You're waiting for something to shatter the tension, but you're not sure what that could be.

Turn to page \nbref{two} if you hear someone say the name "\cIngenuityOld{}".
\end{page}

\begin{page}{two}
In a pinprick of a moment, the tension is gone, and you are awash with goosebumps. The world around you sharpens. Your mind sharpens. \cIngenuityOld{}. The name sounds similar to yours, but not entirely. Still, it feels familiar like a warm embrace from a family member. You know every inch of it. Not just \cIngenuityOld{}. It is \cIngenuityOld{\intro}... a family name with no form prefix, not one of the Silverside family names. It must be an old humanity name! But then why does it feel so familiar to you?

When you have looked at two old humanity artifacts, turn to page \nbref{three}.
\end{page}

\begin{page}{three}
You don't know how, but you are certain of it. \cIngenuityOld{\intro} is your name. \emph{Was} your name. And there's another name on the tip of your tongue. A name that gives you butterflies in your stomach. Someone you loved, a long, long time ago. Somehow. You went on a journey with \cIngenuityOld{\them}. A dangerous journey that led to here. Led to Silverside. But how could you have done such a thing? Silverside is the last city on Earth. And that's the way it has been for over 300 years...

All of a sudden it comes to you. The one you loved, \cSavior{\they} founded Silverside. With you. In another life, another time. Is it really possible that people can live multiple lives?

When you have asked two people about the founders of Silverside, turn to page \nbref{four}.
\end{page}

\begin{page}{four}
\emph{\cSavior{}}. \cSavior{\intro} was her name. \cSavior{\They} was yours and you were \cIngenuity{\theirs}. You met \cSavior{\them} in the ruins of Chicago, abandoned by most after the Tulley-Scott asteroid had devastated the Midwest 20 years prior. But not the Ekkilons, who made their homes on the tops of submerged skyscrapers. \cSavior{\They} arrived when the revivified corpses began to rise from the Great Inland Sea. \cSavior{} rescued you after the rest of your family was pulled underwater by skeletal hands. You traveled together after that, stealing boats, battling endtimes cults, sheltering from megastorms and more. You were a team, and you, \cIngenuityOld{}, could hold your own. Because you were Ingenuity, in the same way that \cSavior{\they} was the Savior.

When you have talked to someone willing to discuss "archetypes" with you for two minutes, turn to page \nbref{five}.
\end{page}

\begin{page}{five}
You eventually began to feel the same pull that \cSavior{} told you \cSavior{\they} experienced, an impulse to converge on a single point. Even \cSavior{\they} didn't know why, just that we had to save as many people as we can and lead them there. You could sense that there were others like you, leading similar groups. 

Many were unwilling to follow you. In the end you only had a few hundred people, when you reached Colorado Springs and passed it, heading into the mountains, where you found a great crowd. You asked \cSavior{\them}, \emph{why there, and not the city?} \cSavior{\They} said \cSavior{\they} weren't strong enough to save it. \cSavior{\They} looked down at her sword, the one \cSavior{\they} called Loyalty, and wept.

When you have seen item 00017 or the character with badge number 00017, turn to page \nbref{six}.
\end{page}

\begin{page}{six}
It was only a short time before the End came, the final asteroid that would destroy everything. Everything, of course, but your huddled crowd. Because you had The Savior. Dess couldn't save everyone. The odds were against \cSavior{\them}. But humanity was not going to end on our watch.

In the end, it was all on \cSavior{\them}. As the sky lit on fire and the waves of sound and water crashed, \cSavior{\they} pierced the ground with Loyalty using all \cSavior{\their} strength. A dome arose around us, holding back the waves until they subsided, and \cSavior{\they} collapsed into the dirt.

You comforted \cSavior{\them}, taking your eyes off Loyalty. When you looked back, there was a baby in its place. You had a \cLoyalty{\offspring}, you and your Dess. Born of the End, of Loyalty, we called \cLoyalty{\them} \cLoyalty{\intro}.

Add +1 to your $\alpha$.
\end{page}

\endnotebook

\end{document}
