\documentclass[greennotebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nLoveGreenTwo{}}

\begin{page}{first}
A love song is singing in your ear, lightly, almost a whisper. It sings like a story, told through the ages, like when you touch an artifact from before the End and record it as Historians do. But this is different. The whisper is insistent that you hear it, and is loudest of all in this strange complex. It is calling to you. Ancient, but ageless. A romance between two people, whose names are on the tip of your tongue, but you can't quite remember them.

If you hear the name \cIngenuityOld{} first, turn to page \nbref{two}. If you hear the name \cSavior{} first, turn to page \nbref{three}.
\end{page}

\begin{page}{two}
Yes, of course! \cIngenuityOld{\intro}! It sounds strange in your mind, but it is definitely a name. An old name... from before the End, before the family name system took form. \emph{\cIngenuityOld{}...}

Your mind is pulled to another place, another time. You are on a boat, paddling in between the tops of skyscrapers in a flooded city. Chicago. Yes, the old city was devastated by the Tulley-Scott asteroid, 20 years before the End. Most people didn't come back to the sunken city after the strike. But the Ekkilons did, making their livings diving for salvage. They thought they were safe when they heard stories of panic and disaster. But they were wrong. By the time the dead began to rise, skeletal in form, from the deep, it was already too late for all but \cIngenuityOld{}, whose eyes you see from. Just as their fingers grabbed at her feet as she tried to get out of her canoe and onto a roof, a hand came from above, still covered in flesh. It was then she made eye contact with her Savior, and there was a spark between them. \cSavior{}.

When you hear the word "Ingenuity", turn to page \nbref{four}.
\end{page}

\begin{page}{three}
Yes, of course! \cSavior{\intro}! It sounds strange in your mind, but it is definitely a name. An old name... from before the End, before the family name system took form. \emph{\cSavior{}...}

Your mind is pulled to another place, another time. You are on a rooftop, a rooftop of a building that once stretched to the sky. Now it's mostly underwater. Because of the asteroid, Tulley-Scott, a harbinger before the Harbinger. You see evidence of people living in in the buildings. Not many people, but some. Perhaps they would let you stay for a night. But something was wrong. It seemed like there had been a struggle... You hear a scream, and run to the edge of the building and look over. There is a girl, with a skeletal hand trying to get a grip on her ankle. You reach out for her hand and make eye contact. There is a spark between you. She snaps out of it, and you pull her up. \cIngenuityOld{} is her name. Her family didn't make it, and all of the boats had been disabled. But, in her Ingenuity, she fixes one, and you escape the beleaguered city together.

When you hear the word "Savior", turn to page \nbref{five}.
\end{page}

\begin{page}{four}
"Ingenuity" means something, doesn't it? It's something vital about the person whose life you were pulled into so abruptly. \cIngenuityOld{} \emph{is} Ingenuity, somehow. Or was.

She fell in love with the Savior, as they undertook a dangerous journey, collecting refugees as they went. As time went on, Ingenuity saved the Savior, who was unprepared for the journey, carrying only the clothes on \cSavior{\their} back and a sword... a sword called Loyalty. Ingenuity saved \cSavior{\them} a lot. But it was Loyalty that saved them all, that brought them together. Because Loyalty wasn't just a sword, but an archetype, like the rest of them, like the other leaders who brought people from the four corners of the continent to a single spot. They were drawn to the Rocky Mountains of Colorado. That's where they made their last stand against the apocalypse.

When you have talked to two people about "archetypes", turn to page \nbref{six}.
\end{page}

\begin{page}{five}
"Savior" means something, doesn't it? It's something vital about the person whose life you were pulled into so abruptly. \cSavior{} \emph{is} the Savior, somehow. Or was.

She fell in love with the Ingenious girl, as they undertook a dangerous journey, collecting refugees as they went. As time went on, the Savior was saved by Ingenuity a lot, since she was unprepared for the journey, carrying only the clothes on \cSavior{\their} back and a sword... a sword called Loyalty. In the end, Loyalty brought them both together, and saved them all. Because Loyalty wasn't just a sword, but an archetype, like the rest of them, like the other leaders who brought people from the four corners of the continent to a single spot. They were drawn to the Rocky Mountains of Colorado. That's where they made their last stand against the apocalypse.

When you have talked to two people about "archetypes", turn to page \nbref{seven}.
\end{page}

\begin{page}{six}
Yes, archetypes... Everyone here is one, including you. This is why you are so drawn to stories of Love, because that is what you are. Right now, you are drawn to Ingenuity, because the old archetype of Ingenuity, whose love saved humanity, is here among you again. It's likely she is confused, rediscovering old memories, which will be especially painful, because things are different now. The world is in need of a savior, but no Savior is here. Perhaps you should find Ingenuity.

Add +1 to your $\alpha$ unless you already did on page \nbref{seven}.

If you figure out who Ingenuity is, turn to page \nbref{eight}.
If you would rather focus on Loyalty, turn to page \nbref{seven}.
\end{page}

\begin{page}{seven}
Yes, archetypes... Everyone here is one, including you. This is why you are so drawn to stories of Love, because that is what you are. Right now, you are drawn to Loyalty, because the sword did not remain a sword, after the End. After \cSavior{} used it to pierce the ground with all \cSavior{\their} might, raising a protective shield around the crowd of survivors, it became something else. A child, loved by \cLoyalty{\their} parents \cIngenuityOld{} and \cSavior{}. Because the love of parent for child is love as much as romantic, as much as true friendship. That child is still around, somewhere, though not in the same form.

Add +1 to your $\alpha$ unless you already did on page \nbref{six}.

If you see \iLoyalty{}, turn to page \nbref{nine}. If you see the character with badge number 00017, turn to page \nbref{ten}.
If you would rather focus on Ingenuity, turn to page \nbref{six}.
\end{page}

\begin{page}{eight}
You've found \cIngenuity{\them}! Ingenuity is \cIngenuity{\intro} and was \cIngenuityOld{\intro}. It's complicated to wrap your mind around. Ingenuity is both of these people, but at the same time, \cIngenuity{} is not \cIngenuityOld{}. Or... do you have that backwards? Suffice to say that this archetype thing is tricky to understand. But either way, there's no sign of the Savior in this complex. Or is there?
You get the sense that the Savior is coming again, somehow, someday? Today? But the world could be ending today, should certain other archetypes have their way. You have to make a decision. Is it possible to save the world without a Savior? Is Love of this world and the potential for a better future enough? Combined with the forces of other archetypes? Or will you seek the missing Savior, try to reunite the family that saved humanity from the End?

If you choose to try to reunite the family, add +2 to your $\alpha$ and turn to page \nbref{eleven}.
If you choose to try to save the world yourself (with other archetypes), add +1 to your $\alpha$ and open your L Packet.
\end{page}

\begin{page}{nine}
You've found Loyalty! The sword, the child, the catalyst. But... something is very wrong. Loyalty was once a \cLoyalty{\kid}, but is now a sword again. Something terrible must have happened, a long, long time ago. Something that needs to be reversed. Loyalty protected humanity once, and then became a child. Perhaps... Loyalty could be used to protect humanity again, as long as the sword doesn't fall into the wrong hands. And once the world is safe from archetypes who would see it destroyed, maybe the child will return...

Find the Wielder. If this is not \cIngenuity{}, it may already be too late. Open your L Packet.
\end{page}

\begin{page}{ten}
You've found Loyalty! The sword, the child, the catalyst... and alive once again! But \cLoyalty{\they} is not safe. Not even with \cIngenuity{} around. There's a group that calls themselves the Peacekeepers, who has pledged themselves to keep this family safe. Alert them that you serve the aetheric family, who needs their help. They abhor violence, but they have their ways of protection. You feel the need to do what you can to become stronger to protect \cLoyalty{} and \cIngenuity{}. Open your H Envelope.
\end{page}

\begin{page}{eleven}
A bond forged by time and spark and story and circumstance. A family that found each other, now separated. That is the love story that sings to you to be completed. A vision comes upon you of \cOutcast{\intro}. \cOutcast{\They} is not the Savior. You are certain of that. But the the music is resonating in your head as you contemplate the vision. Go to \cOutcast{}, and ask if you can put a hand on \cOutcast{\their} shoulder. Then you will find what you seek.

(Don't actually physically touch the player without their permission.)
\end{page}

\endnotebook

\end{document}
