\documentclass[notebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nPlagueResearch{}}

\begin{page}{first}
While \cDeath{} has officially barred me from undertaking this research, the opportunity posed by the captive audience in this complex has proven too tempting for me to pass up. I have established in my own self studies that the presence of an archetype in flesh further mutates the biological material. Those in my presence now are my best possible chance for synthesizing a true plague, my greatest desire. I don't actually have to set it loose, but I just need the knowledge that I can do it. And the first step is observation of my subjects.

(When you have observed a character using archetype powers (make sure you have your \iBioKit{}!), turn to page \nbref{two}.)
\end{page}

\begin{page}{two}
Fascinating! I was able to detect the excretion of a novel chemical and increased levels of aetheric energy in the air when the subject used their archetype powers. With my \iBioKit{}, I was able to extract this novel chemical from the air and bottle it.

(Open your C Envelope, then return to this page.)

Now, to analyze the chemical! What secrets could it be hiding? But it looks like I'm missing something necessary for analysis from my \iBioKit{}! I there's probably a \iDiffusionMagnifier{} in the storage room, but I don't have the key! It must have been entrusted to another Council member!

(When you have a \iDiffusionMagnifier{}, turn to page \nbref{three}.)
\end{page}

\begin{page}{three}
That was intensely frustrating, but at least I've got a \iDiffusionMagnifier{} now. Unfortunately, now I've got to find a quiet place to analyze the chemical. It's a delicate process, and has to be started all over again if I'm interrupted. And, of course, I can't let anyone else see me doing it, lest the other Council members find out and chastise me. I can't risk losing this important discovery!

(When you have spent an uninterrupted minute with your \iBioKit{}, the \iDiffusionMagnifier{}, and the \iMysteryChemical{}, turn to page \nbref{four}.)
\end{page}

\begin{page}{four}
These findings are fascinating! Evidence of the archetypal soul's influence on the flesh! I do believe I can manipulate this aetheric-fleshly connection to induce a bodily ailment using my own archetype powers! In other words, I can cause a plague! I know I said before that I don't actually have to set the plague loose, but it seems that this may be my only route to truly knowing it can be done! Ah, and the satisfaction I'll get from witnessing such a sickness! Marvelous! Now, all I need is a test subject. I think I've got this sorted.

(When you have used \aWither{} on a willing or unwilling test subject, turn to page \nbref{five}.)
\end{page}

\begin{page}{five}
Hmm... That didn't work. I mean, my powers did what they usually do, but did not induce any plague symptoms. But I think I know what I was doing wrong! Of course! I can't use an existing power of mine, but must expand myself aetherically in order to create a new ability in myself! It was never something I was very good at, at least compared to my fellows on the Council... but I must try.

Add +1 to your $\alpha$. Your CR is -1 for the next 15 minutes.

Ah! This is not enjoyable at all! But what is this? Those strange spots where I had previously felt uneasiness... these must be the rifts that I've heard others of the Council speaking about. If I stand near one, I might have more success in opening myself to the aetheric maelstrom.

(When you have stood near a rift for 2 minutes, turn to page \nbref{six}.)
\end{page}

\begin{page}{six}
I think I've finally got it! I felt something shift within myself. It feels like a new pool of power within myself, like that I pull from when I \aWither{} or \aDishearten{}. I know I will likely get in trouble if I use it right under my superiors' noses, but it calls to me, oh, it calls to me!

You may now open your P Envelope.
\end{page}

\endnotebook

\end{document}
