\documentclass[notebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nPoison{}}

\begin{page}{first}
Long have I been drawn to the subtle art of poison, but I have never let myself dabble in it up to now. If circumstances were different, I'd do this gradually. The best poisoners slowly introduce poison with a warm meal or refreshing drink, letting the effects appear like a natural decline in health, while the poisoner can be there as comforter, assuring their victim that they can be well again with some more nurturing. I should have been less of a coward. But it's too late for those feelings, because time is running out. I'll have to come up with something more drastic, faster acting. Unfortunately, more obvious. I'll have to think upon how to do this without getting caught.

(After 15 minutes have passed, turn to page \nbref{two}.)
\end{page}

\begin{page}{two}
My former superiors in the Peacekeepers might have looked askance at me for entertaining these thoughts. But I just have a different idea of what constitutes violence. As long as I do not force-feed my targets or raise a hand to them, and they partake of it on their own will, how could this be considered violent? No, it is non-violent justice, my way of caring for my people.

Now, the first step to take is to find something to poison. It appears the Council has laid out a rich feast for us prisoners. I should see that I can acquire a \iVealDinner{} and hide it away.

(When you have a \iVealDinner{}, turn to page \nbref{three}.)
\end{page}

\begin{page}{three}
Okay, I've got the meal to poison. Now I need to find the proper ingredients. It's got to be strong, and I don't know what exactly is available to me in this complex. This place is pristine. They've got to have cleaning supplies somewhere. \iCleaningFluid{} or a \iPolish{} might work as a base. I'll also need a \emph{catalyst}. And a \emph{heat source}.

(When you've collected the necessary items, turn to page \nbref{four}.)
\end{page}

\begin{page}{four}
Now, for the important part. I've got to add the \emph{catalyst} to the base and apply the \emph{heat source}. The reaction might produce fumes that are noxious to breathe, and I've got to be very careful no one sees me synthesizing poison. That first problem I might be able to solve with a \iFaceMask{}. But the second problem might prove more difficult...

(Have all of the items on hand for an interruptible minute, during which it will be obvious to anyone looking at you that you are up to something suspicious. This process is doable without a \iFaceMask{}, but there will be consequences. When the minute is up, tear up the \iVealDinner{} and turn to page \nbref{five}.)
\end{page}

\begin{page}{five}
I've done it! A potent poisoned dish that should be effective almost immediately after being eaten!

(Retrieve a \iPoisonedVeal{} from the OOG X Packet. If you didn't have a \iFaceMask{} when you made the poison, your CR is -1 for the next half hour. The process for making poison detailed in this notebook may be repeated by anyone possessing it.)
\end{page}

\endnotebook

\end{document}
