\documentclass[greennotebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nTraitorGreen{}}

\begin{page}{first}
You feel very uneasy here in this place with all these people. You recognize the feeling. It's something you've felt before in Silverside. Until now, every time you've felt it you were able to escape it before it got too strong. But the uneasiness is stronger here than ever before. There is something or someone here who you don't want to confront, but you don't know why.

Open page \nbref{two} when you see the character with badge number 00013.
\end{page}

\begin{page}{two}
You freeze in place when you see \cIngenuity{\them}. By appearances, a normal, average-looking Shade... but that feels wrong. And \cIngenuity{\their} name, \cIngenuity{}... it's similar, but not quite right, not quite how you're remembering. Remembering? Is this a memory that you've somehow suppressed? Maybe \cIngenuity{} is a nickname. You feel compelled to figure this out. Because the name you remember is \cIngenuityOld{}, and it's calling to you, like a shiver down your spine.

When you've talked to \cIngenuity{} about \cIngenuity{\their} name, turn to page \nbref{three}.
\end{page}

\begin{page}{three}
You are certain of it: \cIngenuity{\intro} is the reason you've been feeling so uneasy. Is this... guilt? But why? You're not used to feeling guilty. Betrayal is in your soul. You have a feeling this has something to do with a past life. The Council has told you little about any of the other prisoners, so you are unsure of what their archetypes are. You have to find out what \cIngenuity{} is, and what thing you could have possibly done to \cIngenuity{\them} that it echoes across time and space.

When you know what \cIngenuity{}'s archetype is, turn to page \nbref{four}.
\end{page}

\begin{page}{four}
The Archetype of Ingenuity... You're sure of it. You've encountered \cIngenuity{\them} in a past life. And.... it's coming back to you. You can see \cIngenuity{\intro}—no—\cIngenuityOld{\intro}. \cIngenuityOld{\They} is with someone else, another old humanity \cSavior{\human} with short, brown hair, wearing a long skirt and corset. They are holding hands. Kissing. And in front of them, a young \cLoyalty{\kid}. The child looks up at you with piercing eyes, and you feel yourself tremble. With what, you are not sure. \cIngenuityOld{} had a \cSavior{\spouse} and a \cLoyalty{\offspring}... and not just any \cSavior{\spouse}. The \cSavior{\human} turns to look at her child, and you feel electricity in your body, numbness in your fingertips. The Savior.

When you have asked two people about the daughter of the Savior, turn to page \nbref{five}.
\end{page}

\begin{page}{five}
The daughter... \emph{the} daughter. Her name flashes into your mind. \cLoyalty{\intro}. She was an archetype too. You knew her, when she was a child and when she was older. But then... she never did get old. You were the same age. You grew up together, attended the first school in Silverside. You were friends, the closest of friends. Then you came into your powers at the turn of adulthood, and you did something terrible.

When you know the archetype of \cLoyalty{}, turn to page \nbref{six}.
\end{page}

\begin{page}{six}
The archetypes of the apocalypse—the future Council—they came to you. Offered you power beyond your wildest dreams. All you had to do was fill the role that fate intended for you: The Traitor. All you had to do was kill your dearest friend. They told you she would come back to you in another life, because she was like you; powerful. They lied. When you slit her throat in her own bed, her eyes opened wide with your betrayal. She wasn't supposed to wake up before it was over! As she died, she disappeared in a flash of light. In her place, a sword that hasn't moved from that spot since. 

Add +1 to your $\alpha$.
\end{page}

\endnotebook

\end{document}
