\documentclass[greennotebook]{Silversiders} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nWisdomGreenTwo{}}

\begin{page}{first}
You may open \nbref{two} if you have been initiated into the Knights of the Silverside.
\end{page}

\begin{page}{two}
What's this? You remember something, something from a long, long time ago. Before this you was born, and another you was old. Something terrible was coming, the Harbinger of the End. It was smaller than Tulley-Scott, but still big enough to wipe out the coast. You had so little time to find her.

The memory fades... what could it mean? What is the Harbinger of the End? And Tulley-Scott?

You may open \nbref{three} as soon as you ask a fellow Historian about what the Harbinger of the End or Tulley-Scott mean.
\end{page}

\begin{page}{three}
You were in a place called Maine, on the edge of a great body of water. Because \emph{she} was there, lost and confused. The Savior. \cSavior{\intro}. It was your duty to make sure to get her the sword. The Sword Loyalty. That's the only way she would survive. The Knights had entrusted it to you, and you had to succeed. Or else all would be lost.

It fades away again. You need to find out more about the Savior and this sword!

You may open \nbref{four} as soon as you ask two people about the Savior who founded Silverside.
\end{page}

\begin{page}{four}
Eventually, you found her. She was standing on the beach, looking at the sky. The fire was on the horizon, but you found her in time. You couldn't give her a full explanation of the Knights, but gave her enough to get her going West. When she held Loyalty, her skin glowed. Or maybe it was just the flames.

The flames fade, and you're back in the secret complex. What could be causing them, setting the sky on fire?

You may open \nbref{five} as soon as you ask two people about the sword Loyalty.
\end{page}

\begin{page}{five}
The memories flood back, one last time.

You had fulfilled your purpose as the Wise Old Man. The last thing you told her was to keep her grip on the sword when the wave came, and she would be fine. \emph{But what about you?} You smiled. \emph{Maybe we'll see each other again someday. In another life, another time.} And then the asteroid hit the water, and the wave washed you away.

Add +1 to your $\alpha$.
\end{page}

\endnotebook

\end{document}
