%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Abil}{\aTest}{
  \s\MYname	{Test Ability}
  \s\MYtext	{You are a test.}
  \s\MYeffect	{This is a Test.}
  }

\NEW{Abil}{\aSpecial}{
  \s\MYname	{Special Powers}
  \s\MYtext	{You have special powers, as detailed in your \gTest{}
		greensheet.}
  \s\MYeffect	{I have special powers!}
  \s\MYgreens	{\gTest{}}
  \suite
  }

\NEW{Abil}{\aFiremansCarry}{
  \s\MYname	{Fireman's Carry}
  \s\MYtext	{You can carry a body as if it were two hands bulky.}
  \s\MYeffect	{I can carry this body well.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


  
%% Basic DarkWater-style Martial Attack abilities


%% Everyone has these 5
\NEW{Abil}{\aAssist}{
  \s\MYname	{Assist}
  \s\MYtext	{You can assist someone else's attack.  You must be
		within ZoC of both the attacker and target.  Within two
		seconds of an attack, direct this at the attacker,
		saying ``\MYname'' and your CR.}
  \s\MYeffect	{I assist your attack.}
  }

\NEW{Abil}{\aKnockOut}{
  \s\MYname	{Knock Out}
  \s\MYtext	{You can knock someone out as an attack. Say ``\MYname'' and your CR.}
  \s\MYeffect	{I knock you out.}
  }

\NEW{Abil}{\aWound}{
  \s\MYname	{Wound}
  \s\MYtext	{You can wound someone as an attack. Say ``\MYname'' and your CR.}
  \s\MYeffect	{I wound you.}
  }
  
\NEW{Abil}{\aRestrain}{
  \s\MYname	{Restrain}
  \s\MYtext	{You can restrain someone as an attack.  Say ``\MYname''
		and your CR.  You may freely drag, attack, or killing-blow them.  
		To do anything else, or if your health state changes, incant ``release'' 
		and let them go.}
  \s\MYeffect	{I restrain you.  You are restrained until I incant
		``release.''}
  }

\NEW{Abil}{\aDisarm}{
  \s\MYname	{Disarm}
  \s\MYtext	{You can disarm one item from someone as an attack.  Say
		``\MYname'' and your CR.  Point at the item you want to
		disarm.  If the attack works, they must drop that item.}
  \s\MYeffect	{I disarm that item.}
  }

%% the \basecombat macro can be prepended to the Char abils list
%% (in char-LIST.tex)
\def\basecombat{\aKnockOut{}\aWound{}\aAssist{}\aRestrain{}\aDisarm{}}

%% only some people have these

\NEW{Abil}{\aHypnosis}{
  \s\MYname	{Ocular Hypnosis}
  \s\MYtext	{You can hypnotize a Perfect or Bulb if you are able to meet their eyes. A hypnotized individual must do your bidding for five minutes. They will remember this when the hypnosis wears off.}
  \s\MYeffect	{I hypnotize you with my eyes. You must do as I say for the next five minutes. You will remember this when the hypnosis wears off.}
  }

\NEW{Abil}{\aPowerfulHypnosis}{
  \s\MYname	{Powerful Ocular Hypnosis}
  \s\MYtext	{You can hypnotize a Perfect or Bulb if you are able to meet their eyes. A hypnotized individual must do your bidding for five minutes. They will NOT remember this when the hypnosis wears off.}
  \s\MYeffect	{I hypnotize you with my eyes. You must do as I say for the next five minutes. You will NOT remember this when the hypnosis wears off.}
  }

\NEW{Abil}{\aGills}{
  \s\MYname	{Water Breathing}
  \s\MYtext	{You can breathe under water.}
  \s\MYeffect	{I can breathe under water.}
  }
  
\NEW{Abil}{\aGlow}{
  \s\MYname	{Glowing Skin}
  \s\MYtext	{You can light up dark spaces with bioluminescent skin.}
  \s\MYeffect	{My skin glows brightly.}
  }
 
 \NEW{Abil}{\aJumpGlide}{
  \s\MYname	{Jump Glide}
  \s\MYtext	{You can jump high and glide to a rest as long as there is aetheric energy in the air. There is always aetheric energy in the air unless it has been mechanically removed.}
  \s\MYeffect	{I can jump high and glide to a rest.}
  }

\NEW{Abil}{\aFlight}{
  \s\MYname	{Flight}
  \s\MYtext	{I can fly if there is aetheric energy in the air. There is always aetheric energy in the air unless it has been mechanically removed.}
  \s\MYeffect	{I can fly.}
  } 

\NEW{Abil}{\aSmash}{
  \s\MYname	{Smash}
  \s\MYtext	{You can destroy any object with your bare hands unless is is marked as indestructible. 3 uses per game.}
  \s\MYeffect	{I smash the object.}
  }

\NEW{Abil}{\aWither}{
  \s\MYname	{Wither}
  \s\MYtext	{You can temporarily reduce an individual's CR to 1. Usable 3 times per game.}
  \s\MYeffect	{You feel yourself weaken. Your CR is 1 for the next ten minutes.}
  }
  
 \NEW{Abil}{\aDeathGlare}{
  \s\MYname	{Death Glare}
  \s\MYtext	{You can bring any individual to a wounded state regardless of their CR. Usable twice per game.}
  \s\MYeffect	{My gaze is like fire. I wound you. You cannot resist.}
  }
  
\NEW{Abil}{\aDishearten}{
  \s\MYname	{Dishearten}
  \s\MYtext	{You can temporarily reduce an individual's CR to 1. Usable 3 times per game.}
  \s\MYeffect	{You feel your sense of self-preservation disappear. You have no will to defend yourself and cannot use abilities for the next ten minutes. Your CR is now 1.}
  }

\NEW{Abil}{\aHearten}{
  \s\MYname	{Hearten}
  \s\MYtext	{You can counteract any ability that reduces CR/causes weakness in yourself or another person. 10 minute cooldown.}
  \s\MYeffect	{You feel yourself come out of the fog and return to normal.}
  }

\NEW{Abil}{\aRageGaze}{
  \s\MYname	{Rage Gaze}
  \s\MYtext	{You can cause an individual you make eye contact with to immediately attack the nearest person that isn't you. Usable twice per game.}
  \s\MYeffect	{My gaze brings rage to your heart. You must immediately attack the nearest person who isn't me.}
  }

\NEW{Abil}{\aBerzerker}{
  \s\MYname	{Berzerker Frenzy}
  \s\MYtext	{You can double your CR for one attack. Usable twice per game.}
  \s\MYeffect	{I get a wild look in my eyes. I attack with double my strength.}
  }

\NEW{Abil}{\aHeartEyes}{
  \s\MYname	{Heart Eyes}
  \s\MYtext	{You can make someone you make eye contact with fall in love with another person for ten minutes. 30 minute cooldown.}
  \s\MYeffect	{You feel butterflies in your stomach. You fall in love with the person I mention for the next 10 minutes.}
  }
  
\NEW{Abil}{\aRomanceImmunity}{
  \s\MYname	{Romance Immunity}
  \s\MYtext	{You are immune to attempts to make you fall in love.}
  \s\MYeffect	{I'm cannot be infatuated.}
  }

\NEW{Abil}{\aHistorianInitiate}{
  \s\MYname	{Initiate into The Historians}
  \s\MYtext	{You can initiate a new member into The Historians and give them the psychometric ability to read artifacts.}
  \s\MYeffect	{You are now a member of The Historians. You can read the past of objects and can use Historian notebooks.}
  }

\NEW{Abil}{\aTruth}{
  \s\MYname	{Truth Telling}
  \s\MYtext	{You can make someone respond truthfully to a single question. 30 minute cooldown.}
  \s\MYeffect	{You feel compelled to answer truthfully to my question.}
  }

\NEW{Abil}{\aRealityWarp}{
  \s\MYname	{Reality Warp}
  \s\MYtext	{You can bypass the rules on a location sign or object. 1 hour cooldown unless you know otherwise.}
  \s\MYeffect	{Reality shifts around me. I can do the impossible.}
  }

\NEW{Abil}{\aSilverTongue}{
  \s\MYname	{Silver Tongue}
  \s\MYtext	{You can can spin an argument that is guaranteed to convince them of a position or take an action. Usable twice per game.}
  \s\MYeffect	{I am very convincing. You must take my side in an argument or take the action I suggest.}
  }

\NEW{Abil}{\aWiseWords}{
  \s\MYname	{Wise Words}
  \s\MYtext	{You can dispense sage advice that increases the CR of all within ZoC of you by 1 for 5 minutes. 30 minute cooldown.}
  \s\MYeffect	{My words of wisdom enlighten you. Your CR is +1 for 5 minutes.}
  }

\NEW{Abil}{\aAppeal}{
  \s\MYname	{Appeal to Culture}
  \s\MYtext	{You can convince a fellow member of your form to take your side in an argument when it favors Bulbs. Usable 3 times per game.}
  \s\MYeffect	{I appeal to you as a fellow member of your form. You must take my side in this argument when it favors your form.}
  }

\NEW{Abil}{\aHeal}{
  \s\MYname	{Healing}
  \s\MYtext	{You can heal someone from a wounded state.}
  \s\MYeffect	{I heal your wounds with glowing hands.}
  }
  
  \NEW{Abil}{\aWake}{
  \s\MYname	{Awakening}
  \s\MYtext	{You can awaken someone from a knocked out state.}
  \s\MYeffect	{I wake you up with glowing hands.}
  }
  
\NEW{Abil}{\aFirstAid}{
  \s\MYname	{First Aid}
  \s\MYtext	{You can heal someone from a wounded state.}
  \s\MYeffect	{I use my first aid skills to tend your wounds. You are no longer wounded.}
  }

\NEW{Abil}{\aFix}{
  \s\MYname	{Fix}
  \s\MYtext	{You can fix a broken object within a minute of it breaking.}
  \s\MYeffect	{I cleverly fix the broken object.}
  }

\NEW{Abil}{\aTech}{
  \s\MYname	{Tech Wizardry}
  \s\MYtext	{You can bypass the time requirement to build a mechanical device.}
  \s\MYeffect	{I somehow manage to get the device built and working almost immediately.}
  }

\NEW{Abil}{\aInvisibility}{
  \s\MYname	{Invisibility}
  \s\MYtext	{You can become invisible for up to ten minutes. Go Not Here when you use this.}
  \s\MYeffect	{I disappear.}
  }  
  
\NEW{Abil}{\aIllusion}{
  \s\MYname	{Illusion}
  \s\MYtext	{You can make one person see something that isn't there. 10 minute cooldown.}
  \s\MYeffect	{You see exactly what I describe.}
  }

\NEW{Abil}{\aShiny}{
  \s\MYname	{Shiny Shiny}
  \s\MYtext	{You can make one person obsess over something or someone for 5 minutes. 10 minute cooldown.}
  \s\MYeffect	{You obsess over what I say for the next 10 minutes.}
  }

\NEW{Abil}{\aPowerfulIllusion}{
  \s\MYname	{Powerful Illusion}
  \s\MYtext	{You can make everyone in a room see something that isn't there. Usable twice per game.}
  \s\MYeffect	{You all see exactly what I describe.}
  }

\NEW{Abil}{\aShadyDisarm}{
  \s\MYname	{Shady Disarm}
  \s\MYtext	{You can disarm one item from someone without their awareness. They must drop that item. 10 minute cooldown.}
  \s\MYeffect	{I disarm that item without you noticing. You cannot resist.}
  }
  
\NEW{Abil}{\aLaughAttack}{
  \s\MYname	{Laugh Attack}
  \s\MYtext	{You can make someone laugh uncontrollably for a minute. 10 minute cooldown.}
  \s\MYeffect	{You begin to laugh uncontrollably for a minute.}
  }

\NEW{Abil}{\aJusticeHunger}{
  \s\MYname	{Hunger for Justice}
  \s\MYtext	{You can make someone attack in favor of a cause they have admitted to you. 3 uses per game.}
  \s\MYeffect	{You feel hungry for justice. Attack the person I tell you if it supports a belief you have admitted to me.}
  }

\NEW{Abil}{\aFleshHunger}{
  \s\MYname	{Hunger for Flesh}
  \s\MYtext	{You can make someone hunger for flesh and attempt to wound all but yourself and those you command them to not harm. One use per game.}
  \s\MYeffect	{You feel an all-encompassing hunger for flesh for the next ten minutes. Attempt to wound all but me and those I direct you not to harm.}
  }

\NEW{Abil}{\aPlague}{
  \s\MYname	{Plague}
  \s\MYtext	{You can infect a person with a weakening plague. Their CR is reduced to 1 for 10 minutes unless healed. Anyone the infected person interacts with contracts the plague unless immune. Tell them to open their P Envelope. This ability can only be used for 10 minutes after receiving it unless you know otherwise.}
  \s\MYeffect	{You contract the plague. Your CR is reduced to 1. Roleplay sickness. You have a strange desire to spread your illness.}
  }
  
\NEW{Abil}{\aImmunity}{
  \s\MYname	{Immunity}
  \s\MYtext	{You are immune to infectious diseases.}
  \s\MYeffect	{I am immune to infectious diseases.}
  }

\NEW{Abil}{\aClairvoyance}{
  \s\MYname	{Clairvoyance}
  \s\MYtext	{You can learn something about a person by speaking with them for 2 minutes. Open the envelope with their name on it. 10 minute cooldown.}
  \s\MYeffect	{I get a far-off look in my eyes.}
  }

\NEW{Abil}{\aProphecy}{
  \s\MYname	{Prophecy}
  \s\MYtext	{You can open one of your prophecy envelopes. You must speak the words aloud in a monotone voice. 30 minute cooldown.}
  \s\MYeffect	{I get a far-off look in my eyes and speak in a monotone voice.}
  }

\NEW{Abil}{\aChannel}{
  \s\MYname	{Channel the Architect}
  \s\MYtext	{You can call upon the strength of the Architect. Your CR doubles for one attack, but is -1 for the rest of the game afterwards. You can only use this power if you have at least 2 CR.}
  \s\MYeffect	{A foreign, strange look passes over my eyes. I attack with double my strength.}
  }

\NEW{Abil}{\aRousingSpeech}{
  \s\MYname	{Rousing Speech}
  \s\MYtext	{You give a rousing pep talk. Roleplay for one minute. Anyone listening agreeing with you has +1 CR for 10 minutes. 30 minute cooldown.}
  \s\MYeffect	{Your determination rises at my words. Your CR raises +1 for 10 minutes if you agree with me.}
  }

\NEW{Abil}{\aGuiltTrip}{
  \s\MYname	{Guilt Trip}
  \s\MYtext	{You can make anyone feel guilty about something they have done, if they have done it, for 10 minutes. 3 uses per game.}
  \s\MYeffect	{You feel intensely guilty about the action I point out if you have done it.}
  }
  
\NEW{Abil}{\aMistakenIdentity}{
  \s\MYname	{Mistaken Identity}
  \s\MYtext	{You can convince one person that another person you point at, including yourself, is someone else for 10 minutes. Usable twice per game.}
  \s\MYeffect	{The person I point at is who I say they are. You believe this for ten minutes.}
  }

\NEW{Abil}{\aFalseIdentity}{
  \s\MYname	{False Identity}
  \s\MYtext	{You can convince anyone that you are who you say you are for 5 minutes. 2 uses per game.}
  \s\MYeffect	{I am who I tell you I am. You believe this for 5 minutes.}
  }

\NEW{Abil}{\aBackstab}{
  \s\MYname	{Backstab}
  \s\MYtext	{You can immediately knock out a person who has admitted something to you in confidence. They won't remember. 3 uses per game.}
  \s\MYeffect	{You are knocked out. You cannot resist, and will not remember when you wake up.}
  }

\NEW{Abil}{\aThrow}{
  \s\MYname	{Throw}
  \s\MYtext	{You can throw someone as an attack. Say ``\MYname'' and
		your CR. Point in the direction you want to throw them.}
  \s\MYeffect	{I throw you. Go in the direction I point ten full steps
		or until you hit a wall or similar.}
  }
  
\NEW{Abil}{\aTough}{
  \s\MYname	{Tough}
  \s\MYtext	{You can resist a single killing blow per game.}
  \s\MYeffect	{I resist your killing blow.}
  }
  
\NEW{Abil}{\aScavenge}{
  \s\MYname	{Scavenge Rift}
  \s\MYtext	{You can see rifts in the fabric of reality, and reach through them to scavenge items, no matter what your $\alpha$ is.}
  \s\MYeffect	{I reach into the rift.}
  }

\NEW{Abil}{\aProtection}{
  \s\MYname	{Protection}
  \s\MYtext	{You protect a character from an attack such that the attack will fail. Usable twice per game. Show this card to the attacker.}
  \s\MYeffect	{Your target is under my protection. Your attack fails.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%