%%%%%
%%
%% This file sets up the Mem, MemFold, and MemEnvelope datatypes, and
%% creates possible macros for each.
%%
%% The Mem datatype isn't really used directly; it's there so the
%% other datatypes can inherit and share its code.
%%
%%%%%

\DECLARESUBTYPE{Mem}{Element}
\PRESETS{Mem}{
  %% \MYname is the trigger
  \F\MYtext	%%  text
  }


%%%%%
%% MemFold and MemEnvelope are both subtypes of Mem.  MemFold is for
%% fold-n-staple style mempackets, MemEnvelope is for stuff-n-seal
%% style mempackets.  If you want a mempacket to contain interesting
%% contents, like sheets, abilities, and other mempackets, use a
%% MemEnvelope.
\DECLARESUBTYPE{MemFold}{Mem}
\DECLARESUBTYPE{MemEnvelope}{Mem}


%%%%%
%% MemCover and MemPage are for the cover and pages of mempacket
%% booklets, which resemble research notebooks.  These are good
%% substitutes for large piles of MemFolds, and can be useful for
%% things like amnesiac characters.
%%
%% Like MemFolds, MemPages shouldn't directly own any other elements
%% as contents.  Use MemEnvelope instead.
%%
%% MemPages are usually assigned to a MemCover (via \MYmems), with the
%% MemCover representing the entire booklet and assigned to a
%% character.
%%
%% A MemCover is not a mempacket in and of itself; its name is not its
%% trigger and its text is not a memory.
\DECLARESUBTYPE{MemCover}{Mem}
\PRESETS{MemCover}{
  \sd\MYtext	{Each page is a memory/event packet with a separate
		trigger.}
  }

\DECLARESUBTYPE{MemPage}{Mem}


%%%%%
%% \memfold{<trigger>}{<text>}
%% \memenvelope{<trigger>}{<text>}
%% \memcover{<name>}{<pages>}
%% \mempage{<trigger>}{<text>}
%% \startmembook{<name>} <pages> \endmembook
%%
%% These are wrappers around \INSTANCE, useful as 1-shots.
%% \startmembook...\endmembook is a simple wrapper around \memcover
%% that may have better syntax for use within character sheets (inside
%% a \starttag{mems}...\endtag block).
\newinstance{MemFold}{\memfold[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemEnvelope}{\memenvelope[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{MemCover}{\memcover[2]}{
  \s\MYname{#1}\s\MYmems{#2}}
\newinstance{MemPage}{\mempage[2]}{
  \s\MYname{#1}\s\MYtext{#2}}

\long\def\startmembook#1#2\endmembook{\memcover{#1}{#2}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{MemFold}{\mTest}{
  \s\MYname	{Test Trigger}
  \s\MYtext	{This is a Test of a fold-n-staple memory packet}
  }
  
  
%% The Sword Loyalty and Archetype Objects

\NEW{MemEnvelope}{\mLEnvelope}{
  \s\MYname	{Open if you try to pick up item 00017}
  \s\MYtext	{You pick up the sword, and you feel a rush of certainty. You are its Wielder... and something more.}
  \s\MYgreens	{\gLoyalty{}}
  }

\NEW{MemFold}{\mLoyalty}{
  \s\MYname	{Open if you try to pick up item 00017}
  \s\MYtext	{Unless you are currently its Wielder, your hand passes through the sword. You cannot pick it up.}
  }
 
 \NEW{MemFold}{\mKEnvelope}{
  \s\MYname	{Open if you kill another character, every time you kill a character.}
  \s\MYtext	{You see the one you killed disappear in a flash of light. If it is \cTruth{}, \cDeath{}, \cWar{}, \cFamine{}, \cPestilence{}, \cLove{}, \cBeauty{}, \cHonor{}, \cIngenuity{}, or the character with badge number 00017, open your K packet.}
  }

 \NEW{MemFold}{\mKPacket}{
  \s\MYname	{K Packet - Only open if directed}
  \s\MYtext	{In the place of the person you killed is an object. If you pick it up, you will receive the unique powers of the one you killed as long as you hold it. If anyone takes it from you or you give it up, those powers pass to them.}
  }
  
\NEW{MemFold}{\mWEnvelope}{
  \s\MYname	{Open if you see another character's death.}
  \s\MYtext	{You see the one killed disappear in a flash of light. If it is \cTruth{}, \cDeath{}, \cWar{}, \cFamine{}, \cPestilence{}, \cLove{}, \cBeauty{}, \cHonor{}, \cIngenuity{}, or the character with badge number 00017, open your W packet.}
  }

 \NEW{MemFold}{\mWPacket}{
  \s\MYname	{W Packet - Only open if directed}
  \s\MYtext	{In the place of the person you saw killed is an object. If you pick it up, you will receive the unique powers of the one killed as long as you hold it. If anyone takes it from you or you give it up, those powers pass to them.}
  }
  
  
%% Oracle Packets

\NEW{MemCover}{\mOracleMems}{
  \s\MYname	{Clairvoyance Discoveries}
  \s\MYmems	{\mCTruth{}\mCWisdom{}\mCDeath{}\mCWar{}\mCFamine{}\mCPestilence{}\mCLove{}\mCTrickster{}\mCMuscle{}\mCCaregiver{}\mCBeauty{}\mCOutcast{}\mCIngenuity{}\mCTraitor{}\mCHonor{}\mCLoyalty{}}
  }

\NEW{MemPage}{\mCTruth}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00001.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCWisdom}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00002.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCDeath}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00003.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCWar}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00004.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCFamine}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00005.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCPestilence}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00006.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCLove}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00007.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCTrickster}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00008.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCMuscle}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00009.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCCaregiver}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00010.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCBeauty}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00011.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCOutcast}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00012.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCIngenuity}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00013.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCTraitor}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00014.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCHonor}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00015.}
  \s\MYtext	{}
  }

\NEW{MemPage}{\mCLoyalty}{
  \s\MYname	{Open when you've used your Clairvoyance ability on the character with badge number 00017.}
  \s\MYtext	{}
  }


%% Famine Ability Envelopes

\NEW{MemEnvelope}{\mGEnvelope}{
  \s\MYname	{E Envelope - Open if told to do so}
  \s\MYtext	{You feel that you're finally on a path that makes sense to you. You are a villain in this story, and now you have a new ability to match that role.}
  \s\MYabils	{\aFleshHunger{}}
  }

\NEW{MemEnvelope}{\mEEnvelope}{
  \s\MYname	{G Envelope - Open if told to do so}
  \s\MYtext	{You feel that you're finally on a path that makes sense to you. You are a hero in this story, and now you have a new ability to match that role.}
  \s\MYabils	{\aJusticeHunger{}}
  }


%% P Envelope
\NEW{MemEnvelope}{\mPEnvelope}{
  \s\MYname	{P Envelope - Open if told to do so}
  \s\MYtext	{You're now infected with the Plague! Your CR is now 1 for the next 10 minutes and you should roleplay being sick. You have a strange desire to spread the Plague using the enclosed ability. You are also now immune to catching the Plague again.}
  \s\MYabils	{\aPlague{}\aImmunity{}}
  }
 
\NEW{MemEnvelope}{\mPPEnvelope}{
  \s\MYname	{P Envelope - Open if told to do so}
  \s\MYtext	{You can feel the infectious power flowing through your veins! You can now infect people with the Plague, using the enclosed ability.}
  \s\MYabils	{\aPlague{}}
  }
 
%% Other Envelopes

\NEW{MemEnvelope}{\mCEnvelope}{
  \s\MYname	{C Envelope - Open if told to do so}
  \s\MYtext	{You managed to isolate a chemical excreted by fleshly archetypes when they use their powers!}
  \s\MYitems	{\iMysteryChemical{}}
  }

\NEW{MemFold}{\mLPacket}{
  \s\MYname	{L Packet - Open if told to do so}
  \s\MYtext	{You can feel the power of Love flowing through your being. Add +1 to your CR for the rest of the game.}
  }
  
\NEW{MemEnvelope}{\mHEnvelope}{
  \s\MYname	{H Envelope - Open if told to do so}
  \s\MYtext	{You can feel the power of Love flowing through your being, and a strong desire to use it to protect. Use this enclosed ability to do that.}
  \s\MYabils	{\aProtection{}}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

